% ------------------------------------------------------------------------------------------------------------------
% Basic configuration of Beamera class and Jagiellonian theme
% ------------------------------------------------------------------------------------------------------------------
\RequirePackage[l2tabu, orthodox]{nag}



\ifx\PresentationStyle\notset
  \def\PresentationStyle{dark}
\fi



% Options: t - align frame text to the top.
\documentclass[10pt,t]{beamer}
\mode<presentation>
\usetheme[style=\PresentationStyle]{jagiellonian}




% ------------------------------------------------------------------------------------
% Procesing configuration files of Jagiellonian theme located
% in the directory "preambule"
% ------------------------------------------------------------------------------------
\input{./preambule/LanguageSettings/JagiellonianPolishLanguageSettings.tex}
\input{./preambule/TextposConfiguration/TextposConfiguration.tex}

\input{./preambule/ImportingLocalPackages.tex}

\input{./preambule/JagiellonianCustomizationGeneral.tex}
\input{./preambule/JagiellonianCustomizationCommands.tex}










% ------------------------------------------------------
% BibLaTeX
% ------------------------------------------------------
% Package biblatex, with biber as its backend, allow us to handle
% bibliography entries that use Unicode symbols outside ASCII.
\usepackage[
language=polish,
backend=biber,
style=alphabetic,
url=false,
eprint=true,
]{biblatex}

\addbibresource{Systemy-operacyjne-Bibliography.bib}





% ------------------------------------------------------
% Importing packages, libraries and setting their configuration
% ------------------------------------------------------





% ------------------------------------------------------
% Local packages
% ------------------------------------------------------
% Local configuration of this particular presentation
\usepackage{./Local-packages/local-settings}










% ------------------------------------------------------------------------------------------------------------------
\title{Systemy operacyjne}
\subtitle{Basics of Java}

\author{Kamil Ziemian \\
  \email}


% \date{}
% ------------------------------------------------------------------------------------------------------------------










% ####################################################################
% Beginning of the document
\begin{document}
% ####################################################################





% ######################################
% Number of chars: 43k+, 22k+,
% Text is adjusted to the left and words are broken at the end of the line.
\RaggedRight
% ######################################





% ######################################
\maketitle
% ######################################





% ##################
\begin{frame}
  \frametitle{Table~of contents}


  \tableofcontents

\end{frame}
% ##################










% ######################################
\EndingSlide{This presentation isn't finished.}
% ######################################










% ######################################
\section{Java background}
% ######################################


% ##################
\begin{frame}
  \frametitle{Historical background}


  $1972$, the first public version of C programming language is released,
  the main designer was
  \colorhref{https://en.wikipedia.org/wiki/Dennis\_Ritchie}{Dennis Ritchie}
  ($1941\text{--}2011$).

  $1985$, the C++ language designed by
  \colorhref{https://en.wikipedia.org/wiki/Bjarne_Stroustrup}
  {Bjarne Stroustrup} (b.~$1950$) enters the stage.

  $1995$, the Java programming language was created
  by~\colorhref{https://en.wikipedia.org/wiki/James\_Gosling}
  {James Gosling} (b.~$1955$).

  Why this timeline is important? Because language C++ was intended to be
  improved~C (this is why it is named ``C plus plus''), while Java was very
  heavily influenced by~C++. To be clear Java \alert{wasn't} designed to
  replace C++, but both good and controversial parts of C++ influenced it
  a~lot.

  Current version of Java is Java $24$ released at March $2025$. Peculiar
  feature of Java is that as today, \currentYear, four other version of Java
  are still supported, which is a~big number for a~language.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Java popularity}


  Today, \currentYear, outside the newest release Java $24$, supported are
  also Java~$8$ (released~$2014$), Java $11$ (released~$2018$), Java $17$
  (released~$2021$) and Java $23$ (released~$2023$).

  Why so many version? It steams mostly for popularity of Java. If you have
  a~lot of code written in some version of language, you want it to keep
  working. At~the~same time you may don't want to updating it to work in
  newer version of the~language. It creates pressure for the~maintainers of
  Java to keep old version of the~language running.

  The~\colorhref{https://www.tiobe.com/tiobe-index/}{\textsc{tiobe}
    Programming Community Index} is a~tool that try to measure popularity of
  programming languages. As its the~creators acknowledge this is very hard
  task and \textsc{tiobe} index isn't perfect, but it is still good tool to
  find which languages are the~most popular. From at least $2002$ Java was
  always in the top five languages.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Language popularity at August $2025$}


  It is worth to look at top $10$ languages according to \textsc{tiobe}
  and their percent ratings as for August $2025$ \\
  1) Python, $26.14 \text{\%}$. \\
  2) C++, $9.18 \text{\%}$. \\
  3) C, $9.03 \text{\%}$. \\
  4) Java, $8.59 \text{\%}$. \\
  5) C\#, $5.52 \text{\%}$. \\
  6) JavaScript, $3.15 \text{\%}$. \\
  7) Visual Basic, $2.33 \text{\%}$. \\
  8) Go, $2.11 \text{\%}$. \\
  9) Perl, $2.08 \text{\%}$. \\
  10) Delphi\textbackslash Object Pascal $1.82 \text{\%}$.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Few trivia}


  Java language is infamously verbose. To write any program you need to type
  a~lot~of letters.

  Java language was named after Java coffee, which is a~type of coffee
  from
  \colorhref{https://en.wikipedia.org/wiki/Coffee\_production\_in\_Indonesia}
  {Indonesia}.

  Language
  \colorhref{https://en.wikipedia.org/wiki/C\_Sharp\_(programming_language)}
  {C\#}, created in $2000$ by
  \colorhref{https://en.wikipedia.org/wiki/Anders\_Hejlsberg}{Anders
    Hejlsberg} (b.~$1960$), is very heavily influenced by Java. Old joke
  says, that C\# is not a~language. It is Microsoft environment for Java.

  There is no relation between Java and JavaScript languages. There is
  a~joke that relation between \alert{Java} and \alert{Java}Script is like
  between \alert{car} and \alert{car}pet.
  \colorhref{https://en.wikipedia.org/wiki/Brendan\_Eich}{Brendan Eich}
  (b.~$1961$) the main person behind creating JavaScript explained
  origin~of the~name in the following way
  \parencite{Fin-JS-Brendan-Eich-CEO-of-Brave-Ver-2016}.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Few trivia}


  JavaScript was developed under company Netscape in~$1995$. At this time
  in USA everything related to internet was easy to sell and name of Java
  language was among one of the~hottest that year. According to Eich,
  Netscape decided that including word ``Java'' in the~``JavaScript'',
  because it was a~gimmick, a~free advertisement.

\end{frame}
% ##################










% ######################################
\section{Some technical terms}
% ######################################


% ##################
\begin{frame}
  \frametitle{Implementation}


  The easiest way to tell what things like implementations means, is to use
  some examples. Consider a~bike. We can tell that bike is ``vehicle with
  two wheels that is powered by human muscle using pedals'', which is
  definition good enough for our purpose. At the same time there are many
  different bikes, sold by various companies, in different sizes, made with
  different materials, colors, etc.

  We will said that \textbf{concept} of bike, which is its definition given
  above, has different \textbf{implementations}: every particular bike
  is implementation of abstract concept. We hope that it make meaning~of
  the word ``implementation'' clear enough.

\end{frame}
% ##################










% ######################################
\section{Basics information about Java}
% ######################################


% ##################
\begin{frame}
  \frametitle{Too many versions}


  As we mentioned earlier currently, \currentYear, there are available
  \alert{five} versions of Java: $8$, $11$, $17$, $23$ and $24$. Java
  change a~many, many places in the time span that pass from $1995$ and old
  code more probably than not, will not work in current versions of Java.

  We spend $90\text{\%}$ or more of our course learning Java core
  functionalities, so our code should work in all available versions of
  Java. But you should be aware, that having \alert{five} different
  version~of the~language used at once is a~source of problems. If you use
  feature from Java $17$ in version~$8$ everything will crush and other
  ``funny'' things will happen.

  The~situation can be even worse, since with probability $99.99\text{\%}$
  there are companies that today use unsupported versions of Java. Some
  good programmer wrote it around $2005$ and is still working? So why
  should we update it?

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Modern Java is fast}


  In this course we aim at learning core of Java. This should give you
  solid foundations for learning deeper layers of Java and things like
  ``How to handle different version of Java?''. I~hope that you will
  understand that learning core of Java is already a~big task and going
  beyond that is already too challenging for current course.

  In the past Java was infamous for it slowness, but things change a~lot
  since then and currently, new versions of Java (too many versions ;) are
  among the fastest language on the market.

  To be clear, you can wrote slow code in \alert{every} language. Slowness
  is easy, high speed is hard. But some languages allow you \alert{only}
  to wrote slow code, while other give you a~chance to make you code
  fast. Modern Java is one of the~fastest languages in that sense.
  At this course we will focus on writing Java code that works. The problem
  of writing fast code will be tackled if we found enough time.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Java Code Conventions}


  September 12, 1997,
  https://www.oracle.com/docs/tech/java/codeconventions.pdf

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{OOP, the C++ way}


  Java is
  \colorhref{https://en.wikipedia.org/wiki/Object-oriented\_programming}
  {\textsc{oop}} language from top to bottom. The~acronym \textsc{oop}
  stand of course for ``object-oriented programming'', which was one~of
  the coolest concept in programming for few decades. Maybe still is today.
  This concepts is far more vague that beginners my imagine, so we should
  look at it for a~few moments.

  C++ was probably the~first language that was object-oriented and become
  widely used in various practical fields, so for many people
  ``object-oriented'' is synonymous to ``it works like in C++''. Particular
  Java is heavily influenced by C++, so it is object-oriented in the~same
  way as it.

  There is nothing wrong if for someone \texttt{oop} means ``it's like
  C++'', if she/he understood that it is not the only way possible~of
  doing \textsc{oop}. You don't need to know the other kinds of
  \textsc{oop}, but you should be aware that they exist.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{OOP, the C++ way}


  We also shouldn't waste our time arguing ``Is language X is
  object-oriented or not?''. We~personally adopted broad definition~of
  object-orientation and think that arguing about details should be
  delegated to our free time as a leisure. What we need to know that C++
  and Java way of implementing object-orientation are the~same in kind, but
  not $1:1$ identical. This can be a~subtle distinction, so we look at it
  a~bit more.

  Java adopted C++ way of object-oriented programming, but add it own flavor
  of it. The~main idea of both languages is as follow. The~\textbf{object}
  is a~thing that gather together data and methods that can be used to
  change a~state of data. Let use some example, we will expand on it
  in the~future.

  Consider that we represent a~lamp in our program. We have some date
  about it: the power of the light bubble, current temperature of this
  bubble, information is it on or off, etc.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Our lamp, the~OOP way}


  In Java code we can represent our lamp by variable \texttt{myLamp}. Inside
  it we have variable \texttt{powerOfLightBubble} that contains information
  about the~power of currently used light bubble. We also have methods
  that works on this lamp. First we have method
  \texttt{showLightBubblePower()}. Glossing over details, if we put in our
  code line \\
  \texttt{myLamp.showLightBubblePower();} \\
  we will see on the screen something like \\
  \texttt{Light bubble has 60 W of power.}

  Consider now that representation of our lamp have a~variable named
  \texttt{stateOfLightBubble}, which tell us is a~lamp turn on or off.
  We also have a~method \texttt{showMeLampState()}, that wrote on the screen
  text informing us, is the lamp turn on or off.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Our lamp, the~OOP way}


  In other words, if we put in our code the line \\
  \texttt{myLamp.showMeLampState();} \\
  we will see on the screen \\
  \texttt{The lamp is turn on.} \\
  or \\
  \texttt{The lamp is turn off.}

  It is natural to also have a~methods \texttt{switchLampOn()}
  and~\texttt{switchLampOff()}, which turn lamp on and off. We can use
  first of them by putting in the code line \\
  \texttt{myLamp.switchLampOn();}

  This example can be already hard to understood for the people that didn't
  encounter C++ style \textsc{oop} before, but they shouldn't be worried.
  We will unpack it later in the~course. What is important now is the fact
  that these idea is used both in C++ and Java. Also in languages like
  Python.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Our lamp, the~OOP way}


  At the~same time C++ and Java are not identical and the code that
  allow use to represent lamp in our programs is different in both
  languages. This is basically what we mean when we said that ``one idea
  has different implementations''.

  We now need to leave our lamp and learn basics of Java. When we learn
  enough, we will wrote code representing our lamp.

\end{frame}
% ##################










% ######################################
\section{Jeszcze o~poruszaniu~się po katalogach}
% ######################################


% ##################
\begin{frame}
  \frametitle{Rola systemu operacyjnego}


  Zacznijmy od~przyjęcia, że~jak poprzednio znajdujemy~się w~katalogu
  \texttt{SO-03-A-Polecenia-BASHa-ETC/}. Tak jak system Windows,
  GNU/Linux posiada koncepcję plików ukrytych, czyli takich, które
  normalnie nie~są widoczne dla użytkownika. Ze~względów historycznych,
  przyjęto zasadę, że~jeśli nazwa pliku zaczyna~się od symbolu~„\texttt{.}”
  to plik jest niewidocznych od użytkownika.

  By zobaczyć wszystkie pliki, które zawiera dany katalog należy
  do~polecenia \texttt{ls} przesłać opcję~\texttt{-a}
  (od ang.~\textit{all}). \\
  \texttt{\$ ls -a} \\
  \texttt{.} \quad \texttt{..} \quad \texttt{Data-01.dat} \quad
  \texttt{Data-02.dat} \quad \directoryName{\texttt{Data-for-analysis}} \\
  Widzimy, że~w~katalogu tym mamy dwa pliki ukryte, o~dość osobliwych
  nazwach, jedna kropka i~dwie kropki. Pliki te znajdują~się w~praktycznie
  każdym katalogu w~systemie GNU/Linux, a~ich nazwy to pewnie zaszłość
  historyczna z~lat $70$-tych XX wieku, kiedy pamięć była bardzo mała
  i~każdy symbol~się liczył.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Pliki „\texttt{.}” i~„\texttt{..}”}


  Zgodnie z~zasadą, że~w~systemie GNU/Linux wszystko jest plikiem, a~co nie
  jest plikiem jest procesem, pliki „\texttt{.}” i~„\texttt{..}” pozwalają
  systemowi zarządzać katalogami. Katalog to wszak tylko inny rodzaj pliku.

  Zacznijmy od~pliku „\texttt{.}”. Plik ten oznacza po prostu katalog
  w~którym~się znajdujemy. Co więcej możemy za jego pomocą przejść
  do~katalogu w~którym jesteśmy (czyli nic nie zrobić), za pomocą
  polecenia: \\
  \texttt{\$ cd .} \\
  Jakkolwiek z~praktycznego punktu widzenia to polecenie jest bezużyteczne,
  warto wiedzieć, że~istnieje i~działa poprawnie.

\end{frame}
% ##################








% % ##################
% \begin{frame}
%   \frametitle{Powłoka BASH}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Postęp technologiczny}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Problemy z~bezpieczeństwem}




% \end{frame}
% % ##################










% % ######################################
% \section{Pliki i~procesy}
% % ######################################



% % ##################
% \begin{frame}
%   \frametitle{Pliki i~procesy}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Pliki i~procesy}




% \end{frame}
% % ##################










% % ######################################
% \section{Podstawy pracy z~poziomu powłoki BASH}
% % ######################################



% % ##################
% \begin{frame}
%   \frametitle{BASH nie zna słowa litość}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Zaczynamy}


% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenia}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenia}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{ls}}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{pwd}}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{System plików}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{System plików}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{System plików}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{System plików}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Katalog domowy}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{cd}}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{cd}}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Edycja plików z~pomocą programu gedit}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Okienko gedita}


% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Edytory tekstów}



% \end{frame}
% % ##################










% % ######################################
% \section{Dalsze informacje o~pracy z~BASHem}
% % ######################################


% % ##################
% \begin{frame}
%   \frametitle{Pewne subtelności}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{mkdir}}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{mv}}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Polecenie \texttt{mv}}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Zagrożenia jakie stwarza \texttt{mv}}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Jak rozsądnie korzystać z~\texttt{mv}?}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Opcje (flagi)}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Czemu życie nie może być proste?}




% \end{frame}
% % ##################










% % ######################################
% \section{Autouzupełnianie w~BASHu}
% % ######################################


% % ##################
% \begin{frame}
%   \frametitle{Autouzupełnianie w~BASHu}




% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Autouzupełnianie w~BASHu}



% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Autouzupełnianie w~BASHu}




% \end{frame}
% % ##################










% % ######################################
% \appendix
% % ######################################





% % ######################################
% \EndingSlide{Dziękuję! Pytania?}
% % ######################################










% % ######################################
% \section{Dlaczego BASH~się tak nazywa}
% % ######################################



% % ##################
% \begin{frame}
%   \frametitle{Dlaczego BASH~się tak nazywa?}




% \end{frame}
% % ##################






% % ##################
% \begin{frame}
%   \frametitle{????}




% \end{frame}
% % ##################






% % ##################
% \endingslide???{}
% % ##################



% % % ##################
% % \jagiellonianendslide{?????}
% % % ##################





% ####################################################################
% ####################################################################
% Bibliography

\printbibliography





% ####################################################################
% End of the document

\end{document}
