% ---------------------------------------------------------------------
% Basic configuration of Beamera and Jagiellonian
% ---------------------------------------------------------------------
\RequirePackage[l2tabu, orthodox]{nag}



\ifx\PresentationStyle\notset
  \def\PresentationStyle{dark}
\fi



\documentclass[10pt,t]{beamer}
\mode<presentation>
\usetheme[style=\PresentationStyle]{jagiellonian}



% ---------------------------------------
% Configuration files of Jagiellonian loceted in catalog preambule
% ---------------------------------------
\input{./preambule/LanguageSettings/JagiellonianEnglishLanguageSettings.tex}
\input{./preambule/TextposConfiguration/TextposConfiguration.tex}

\input{./preambule/JagiellonianCustomizationGeneral.tex}
\input{./preambule/JagiellonianCustomizationCommands.tex}










% ------------------------------------------------------
% BibLaTeX
% ------------------------------------------------------
% Package biblatex, with biber as its backend, allow us to handle
% bibliography entries that use Unicode symbols outside ASCII.
\usepackage[
language=polish,
backend=biber,
style=alphabetic,
url=false,
eprint=true,
]{biblatex}

\addbibresource{Stochastic-quantization-and-singular-stochastic-equations-Bibliography.bib}





% ------------------------------------------------------
% Wonderful package PGF/TikZ
% ------------------------------------------------------

% Node and pics for drawing charts
% \usepackage{./Local-packages/PGF-TikZ-Chart-nodes-and-pics}

% Styles for arrows
% \usepackage{./Local-packages/PGF-TikZ-Arrows-styles}

% Pic for drawing functions
% \usepackage{./Local-packages/PGF-TikZ-Functions-pics}






% ------------------------------------------------------
% Local packages
% ------------------------------------------------------
% Special configuration for this particular presentation
\usepackage{./Local-packages/local-settings}

% Package containing various command useful for working with a text
\usepackage{./Local-packages/general-commands}

% Package containing commands and other code useful for working with
% mathematical text
\usepackage{./Local-packages/math-commands}










% ---------------------------------------------------------------------
\title{Stochastic quantization and singular stochastic
  equations}

\author{Kamil Ziemian \\
  \texttt{kziemianfvt@gmail.com}}


% \institute{}

\date[28 XI 2025]{Seminar of Field Theory Department \\
  28 XI 2024}
% --------------------------------------------------------------------










% ####################################################################
% Początek dokumentu
\begin{document}
% ####################################################################





% ######################################
% Number of chars: 29k+, 84k+,
% Text is adjusted to the left and words are broken at the end of the line.
\RaggedRight
% ######################################






% ######################################
\maketitle % Tytuł całego tekstu
% ######################################





% ######################################
\begin{frame}
  \frametitle{Spis treści}


  \tableofcontents % Spis treści

\end{frame}
% ######################################





% ######################################
\section{Constructive QFT and itis problems}
% ######################################





% ##################
\begin{frame}
  \frametitle{Aims of our talk}


  The aim of this talk is twofold. First, we want to justify and give
  overview of procedure called stochastic quantization, that allow us to
  define rigorously some models of quantum fields in $1 + 1$ and $2 + 1$
  dimensions with some promise for future development. This procedure force
  us to deal with \textbf{singular stochastic partial differential
    equations} (SsPDEs for short), which are as complicated to analyze as
  their name is long. Theory of SsPDE is now the research topic of
  Paweł Duch, who was a member of Field Theory Department in the years
  $2012\text{--}2018$. Explaining some of his recent results is the second
  aim of our talk.

  All these topics are very complicated and involve cutting edge
  mathematical research, so we cannot explain them in all the glorious
  details. Our talk is rather a very simple overview of this active field
  of research. Also, you can get PDF of this presentation, writing me an
  e-mail at \texttt{kziemianfvt@gmail.com}.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Mathematical physicists always spoils the fun}


  We want to define a simple quantum field theory like $\Phi^{ 4 }$
  in~$d$~dimensional Minkowski space. So we wrote the lagrangian
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-01}
    \Lcal( x ) =
    \frac{ 1 }{ 2 } \partial_{ \mu } \Phi( x ) \partial^{ \mu } \Phi( x ) - m^{ 2 } \Phi^{ 2 }( x )
    - \frac{ \lambda }{ 4! } \Phi^{ 4 }( x ).
  \end{equation}
  where $x = [ t, x_{ 1 }, x_{ 2 }, \ldots, x_{ d - 1 } ]$ and
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-02}
    x \cdot x = t^{ \, 2 } - x_{ 1 }^{ \, 2 } - x_{ 2 }^{ \, 2 } -
    x_{ 3 }^{ \, 2 } - \ldots - x_{ d - 1 }^{ \, 2 }.
  \end{equation}
  Then we compute action
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-03}
    S[ \Phi( x ) ] =
    \int\limits_{ [ 0, 1 ] \times \Rbb^{ d } } d^{ d + 1 }x \, \Lcal[ \Phi( x ) ],
  \end{equation}
  and partition function
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-04}
    Z[ \, J( x ) ] =
    \int [ \Dcal \Phi( x ) ] \exp\Big( i S[ \phi( x ) ] + i \int d^{ d + 1 }x \, J( x )
    \Phi( x ) \Big),
  \end{equation}
  and we can do physics now. But, mathematical physicists like to spoil
  all the fun, so they point out that measure $[ \Dcal \Phi( x ) ]$ doesn't
  exist.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Why $[ \Dcal \Phi( x ) ]$ doesn't exists?}


  What is the problem with $[ \Dcal \Phi( x ) ]$? First we need to notice,
  that it should be a~Lebesgue's measure for, let say, the infinite
  dimensional space of functions, like $L^{ 2 }( \Rbb^{ d } )$. In the
  case~of $\Rbb^{ d }$ the crucial property of Lebesgue's measure is
  translational invariance. If we have measurable set $A \subset \Rbb^{ d }$, then
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-05}
    \forall \, \vecx \in \Rbb^{ d }, \quad
    \text{vol}( A + \vecx ) = \text{vol}( A ).
  \end{equation}
  More precisely, we have the following theorem. \\
  \textit{Let $G$ be a locally compact, topological group. There
    \alert{exists} translational invariant, positive measure on the $G$,
    which is unique, up to multiplication by constant $c > 0$.}

  Existence of Lebesgue's measure is closely tied to its translational
  invariance, but in infinite dimensional space, we cannot have
  translation invariant measure. Simple argument for that goes as follows.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Finite dimensional space are easy}


  Let $K( 0, \frac{ 1 }{ 4 } )$ will be ball in our space and assume that
  it has non-zero finite measure
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-06}
    0 < \mu\big( K( 0, \tfrac{ 1 }{ 4 } ) \big) < +\infty.
  \end{equation}
  Since $K( 0, \frac{ 1 }{ 4 } ) \subset K( 0, 1 )$, it implies
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-07}
    \mu\big( K( 0, \tfrac{ 1 }{ 4 } ) \big) \leq \mu( K( 0, 1 ) ).
  \end{equation}
  In three dimensional space I can take unite ball
  $K( ( 0, 0, 0 ), \tfrac{ 1 }{ 4 } )$ and create six disjoint balls
  contained inside $K( ( 0, 0, 0 ), 1 )$ by shifting this first ball
  by vectors $[ \frac{ 1 }{ 2 }, 0, 0 ]$, $[ -\frac{ 1 }{ 2 }, 0, 0 ]$,
  $[ 0, \frac{ 1 }{ 2 }, 0 ]$, $[ 0, -\frac{ 1 }{ 2 }, 0 ]$, etc. If our
  measure is translational invariant we arrive at result
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-08}
    6 \, \mu\big( K( ( 0, 0, 0), \tfrac{ 1 }{ 4 } ) \big) \leq
    \mu\big( K( ( 0, 0, 0 ), 1 ) \big).
  \end{equation}
  Which is a perfectly fine result. But in infinite dimensional space,
  we have a serious problem.

\end{frame}
% ##################






% ##################
\begin{frame}
  \frametitle{Infinite dimensional space are hard}


  In infinite dimensional space like $L^{ 2 }( \Rbb^{ 3 }, d^{ 3 }x )$, we
  have infinitely many orthogonal vectors with the length $\frac{ 1 }{ 2 }$
  to perform such shifts. As a~result we have infinitely many disjoint
  balls with radius $\tfrac{ 1 }{ 4 }$ that are contained
  inside unit ball $\mu\big( K( 0, 1 ) \big)$:
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-09}
    K( x_{ i }, \tfrac{ 1 }{ 4 } ) \subset K( 0, 1 ), \quad i \in I,
  \end{equation}
  where $I$ is some infinite set.

  Assuming translational invariance of our measure, we get
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-10}
    \infty \, \mu\big( K( 0, \tfrac{ 1 }{ 4 } ) \big) \leq \mu\big( K( 0, 1 ) \big).
  \end{equation}
  This can only be true in two situations. First
  $\mu\big( K( 0, \tfrac{ 1 }{ 4 } ) \big) = 0$, second
  $\mu\big( K( 0, 1 ) \big) = +\infty$. In first case we have contradiction
  with our assumption $\mu\big( K( 0, \frac{ 1 }{ 4 } ) \big) \neq 0$, so this
  is nonsense. In the second case, we arrived at quite reasonable, but
  useless for all application measures, in which the unit ball in
  infinite dimensional space has infinite volume.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Life is hard, but we don't give up}


  We thus must abandon search for such translational measures, at least
  in Hilbert spaces, since our reasoning was based on having orthogonal
  vectors. More advanced analysis show us, that we should look for
  measures not at the space of functions, but on the spaces of
  distributions, like $\Dcal'( \Rbb^{ n } )$ and $\Scal'( \Rbb^{ n } )$.
  But, we can't go into details.

  This task is very hard, but we don't give up. It will be important
  for the future, that because we know already how to solve the problem of
  \alert{free} field, we can construct measure for \alert{free}
  evolution~of such \alert{free} field. This measure is a functional
  Guassian measure.

  Since our task of finding such measures is very hard, we need to simplify
  it a bit. First of all function in our naive measure
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-11}
    [ \Dcal \Phi( x ) ] \exp\Big( i S[ \Phi( x ) ] \Big),
  \end{equation}
  we have an oscillating function $\exp( i S )$, which of course makes
  such an expression harder to work with.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Euclidian QFT comes for rescue}


  As textbooks of QFT tell us, we should make Wick rotation: $t = i \tau$.
  Which means that our measure is now
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-12}
    [ \Dcal \Phi_{ \text{Euc} }( x_{ \text{Euc} } ) ]
    \exp\Big( -\!S_{ \text{Euc} }[ \Phi_{ \text{Euc} }( x ) ] \Big)
  \end{equation}
  and scalar product of our vectors
  $x_{ \text{Euc} } = [ \tau, x_{ 1 }, x_{ 2 }, \ldots, x_{ d } ]$ is, almost, Euclidian
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-13}
    -x_{ \text{Euc} } \cdot x_{ \text{Euc} } =
    \tau^{ 2 } + x_{ 1 }^{ \, 2 } + x_{ 2 }^{ \, 2 } + \ldots + x_{ d }^{ \, 2 }.
  \end{equation}
  This is why we call it \colorhref{}{Euclidian Quantum Field Theory}
  (EQFT for short). Because naive measure
  \eqref{eq:Stochastic-quantization-ETC-12} is much nicer that
  previous one with $\exp( i S )$ part, a large portion of successes of
  constructive QFT was connected to this approach
  \parencite{Summers-Prespective-on-Constructive-ETC-Pub-2016}.

  We need to mention three more important things. First, you can think
  about EQFT as a stochastic process in the space of distributions. Hard to
  imagine, but you can live with that after the while.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Euclidian QFT comes for rescue}


  Second, Guassian measure of free field in Minkowski space becomes
  Gaussian white noise measure in EQFT. Gaussian white noise, which will
  be denoting $\eta( x_{ \text{Euc} } )$, is a~very important concept for SsPDEs.

  From the point of view of mathematical physics Wick rotation $t = i \tau$ is
  just a bunch of lines on the slide, without any true meaning.
  But \colorhref{https://en.wikipedia.org/wiki/Konrad\_Osterwalder}{Konrad
    Osterwalder} and
  \colorhref{https://en.wikipedia.org/wiki/Robert\_Schrader}{Robert
    Schrader} proved very important reconstruction theorem, which
  states that Euclidean quantum field in $d$~dimensions that fulfils
  given set of requirements, can be transformed into a~quantum field in $d$
  dimensional Minkowski space by analytical continuation
  \parencite{Osterwalder-Schrader-Axioms-for-Euclidean-Part-I-ETC-Pub-1973},
  \parencite{Osterwalder-Schrader-Axioms-for-Euclidean-Part-II-ETC-Pub-1975}.

  This set of requirments is called
  \colorhref{https://en.wikipedia.org/wiki/Schwinger\_function}
  {Osterwalder-Schrader axioms}. The axioms are: temperedness, linear
  growth condition, Euclidian covariance, positivity, symmetry
  and cluster property, but explaining them is far beyond the scope of
  this~talk.

\end{frame}
% ##################










% ######################################
\section{Stochastic quantization}
% ######################################



% ##################
\begin{frame}
  \frametitle{Why stochastic quantization?}


  Stochastic quntization was proposed by
  \colorhref{https://en.wikipedia.org/wiki/Giorgio\_Parisi}
  {Giorgio Parisi} and Yong-shi Wu in the context
  of gauge fields, to avoid the problem of Gribov ambiguities, so we
  need to speak a few words about it. Consider gauge field
  $A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$ and gauge function
  $u( x_{ \text{Euc} } )$. We know, that physical situations described by
  $A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$ and
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-14}
    \begin{split}
      \widetilde{ A }_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )
      &=
        u( x_{ \text{Euc} } )^{ -1 } A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )
        u( x_{ \text{Euc} } ) - \\
      &\quad - \frac{i}{ g } u( x_{ \text{Euc} } )^{ -1 }
        \partial_{ \mu } u( x_{ \text{Euc} } ),
    \end{split}
  \end{equation}
  where $g$ is coupling constant, are the same. So even naive expression
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-15}
    Z[ \, J^{ \sigma }( x_{ \text{Euc} } ) ] =
    \int [ \Dcal A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } ) ]
    \exp\Big( -S[ A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } ) ] \Big),
  \end{equation}
  or its Minkowski analogue are physically incorrect. Such integrals
  counts the same physical situation many times over, because we integrate
  over $A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$ and all possible
  $\widetilde{ A }_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$ connected to it by
  gauge transformation.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Gribov ambiguities}


  Standard way of solving that is gauge fixing. We choose function $G$ over
  the space of fields and integrate only over fields that fulfill equation
  $G( A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } ) ) = 0$. Such a procedure is
  well known from Clerk Maxwell electrodynamics. But as was first observed
  by \colorhref{https://en.wikipedia.org/wiki/Vladimir\_Gribov}{Vladimir
    Gribov}, the example of \alert{abelian} electrodynamics is highly
  misleading. In the case of theory with non-abelian gauge groups there are
  very deep topological reasons that prevent us from making ``resonable''
  gauge fixing
  \parencite{Gribov-Quantization-of-non-Abelian-gauge-theories-Pub-1978},
  \parencite{Singer-Some-Remarks-on-the-Gribov-Ambiguity-Pub-1978}. As a
  result even after imposing the condition
  $G( A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } ) ) = 0$ we can have
  overcounting.

  Parisi and Wu propose to solve that problem, by replacing gauge fixing
  by analysis of stochastic process in the space of \alert{all} fields
  \parencite{Parisi-Wu-Perturbation-Theory-Without-Gauge-Fixing-Pub-1981},
  \parencite{Damgaard-Huffel-Stochastic-quantization-Pub-1987},
  \parencite{Gubinelli-What-is-stochastic-quanstization-ETC-Ver-2022}.
  Simplifying their argument, you \alert{don't} fixe gauge, but evolve
  field in the totally fake time $t_{ \text{F} }$ as a~``diffusion'' process
  in the space of fields in such a~way, that unphysical contribution from
  equivalent fields cancels out.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Why must life be so complicated?}


  To be more concrete, we start from field
  $A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$ and add to it arguments
  totally fake time $t_{ \text{F} }$ to get
  $A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } )$. We now evolve
  this field in fake time according to Langevine equation
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-16}
    \frac{ \partial A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } ) }
    { \partial t_{ \text{F} } } =
    -\frac{ \delta S_{ \text{Euc} } }{ \delta A_{ \text{Euc}, \, \mu } } +
    \eta( t_{ \text{F} }, x_{ \text{Euc} } ),
  \end{equation}
  where $\eta( t_{ \text{F} }, x_{ \text{Euc} } )$ is Gaussian white noise.
  Parisi and Wu postulate that
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-17}
    \lim_{ t_{ \text{F} } \to \infty }
    [ \Dcal A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } ) ] =
    [ \Dcal A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } ) ]_{ \text{phys} },
  \end{equation}
  where on the right hand side you have a physical correct measure for
  the physical field $A_{ \text{Euc}, \, \mu }( x_{ \text{Euc} } )$.

  A~lot of effort was put into making these statements more rigorous.
  The main problem is that $\eta( t_{ \text{F} }, x_{ \text{Euc} } )$ is a very
  singular object, you can think about it as a randomly valued distribution.
  As a result field $A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } )$
  also need to be a~distribution.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Singular stochastic PDEs (SsPDEs)}


  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-18}
    \frac{ \partial A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } ) }
    { \partial t_{ \text{F} } } =
    -\frac{ \delta S_{ \text{Euc} } }{ \delta A_{ \text{Euc}, \, \mu } } +
    \eta( t_{ \text{F} }, x_{ \text{Euc} } ),
  \end{equation}
  If we think about free theory then expression
  $-\delta S_{ \text{Euc} } / \delta A_{ \text{Euc}, \, \mu }$ is linear in distribution
  $A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } )$, so life is great.
  But we know that if we want to have interacting field, we will need
  add least quadratic term in fields, something like
  $\psi_{ \text{Euc} }( t_{ \text{F} }, x_{ \text{Euc} } )
  A_{ \text{Euc}, \, \mu }( t_{ \text{F} }, x_{ \text{Euc} } )$. And we know that
  in general, products of distributions have no sense.

  Such stochastic PDEs that are ill posed because of products of
  distributions are called \alert{singular stochastics PDEs} (SsPDEs)
  and are as complicated as they name is long
  \parencite{Duch-Lecture-notes-on-flow-equation-approach-ETC-Pub-2025}.

\end{frame}
% ##################










% ######################################
\section{SsPDEs and works of Paweł Duch}
% ######################################


% ##################
\begin{frame}
  \frametitle{Making sense of SsPDEs}


  You encounter SsPDEs in various fields of science, so we have good
  reasons to define them mathematically. For us especially important are
  works of Martin Hairer who won
  \colorhref{https://en.wikipedia.org/wiki/Fields\_Medal}{Fields Medal} in
  $2014$ ``\textit{For his outstanding contributions to the theory of
    stochastic partial differential equations, and in particular for
    the creation of a theory of regularity structures for such
    equations}''.

  Hairer and his collaborators first pay attenntion to problems like
  defining \colorhref{https://en.wikipedia.org/wiki/Kardar\%E2\%80\%93Parisi\%E2\%80\%93Zhang\_equation}
  {KPZ equation} (named after Mehran Kadar, Giorgio Paris again ;) and
  Yi-Cheng Zhang), but since they put more attention to QFT
  \parencite{Hairer-Yang-Mills-and-the-Mass-Gap-Ver-2025}. In $2024$
  he together with Ajay Changra, Ilya Chevyrev, Hao Shen published
  article \colorhref{https://arxiv.org/abs/2201.03487}
  {\textit{Stochastic quantisation~of Yang-Mills-Higgs in~3D}}
  \parencite{Chandra-et-al-Stochastic-quantisation-of-Yang-Mills-ETC-Pub-2024}. In August of $2025$ Hairer, Paweł Duch, Jaeyun Yi and Wenhao Zhao
  published on arXiv paper
  \colorhref{https://arxiv.org/abs/2508.07776}
  {\textit{Ergodicity of infinite volume $\Phi_{ 3 }^{ \, 4 }$ at high
      temperature}}
  \parencite{Duch-Hairer-Yi-Zhao-Ergodicity-of-infinite-volume-ETC-Pub-2025}.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Paweł Duch's works on flow equation approach}


  Current works of Paweł Duch focus in large part on flow equation approach
  to SsPDES. It was inspired by renormalization group theory of
  Kenneth Wilson and works of Antti Kupiainen, who adapted it for
  the~case~of stochastic PDEs
  \parencite{Wilson-Renormalization-Group-and-Critical-ETC-Part-I-Pub-1971},
  \parencite{Kupiainen-Renormalization-Group-and-Stochastic-PDEs-Pub-2016}.
  Because the theory of SsPDEs is very complex, for the~purpose of this
  talk, we need to simplify a lot and introduce some notation. This notation
  may not be the most precise, but useful in sketching the~problem.

  We first fix dimension $d$ and denote $d$-dimensional torus by $T^{ d }$.
  Let $V$ be map transforming space of continuous functions on $T^{ d }$
  into itself:
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-19}
    V: \Ccal( T^{ d } ) \to \Ccal( T^{ d } ).
  \end{equation}
  The value of $V$ on function $\varphi \in \Ccal( T^{ d } )$ we will be denoting
  by $V[ \varphi ]$. The derivative of $k$~order of $V$ at $\varphi$ in the direction
  of function $\psi$ is defined as
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-20}
    D^{ k } V[ \varphi ] \cdot \psi^{ \otimes k } :=
    \partial_{ \tau }^{ \, k } \, V[ \varphi + \tau \psi ] \big|_{ \tau = 0 }.
  \end{equation}
  % Current works of Paweł Duch focus in large part on flow equation approach
  % to SsPDES. It was inspired by renormalization group approach of
  % Kenneth Wilson and works of Antti Kupiainen, who addapted it for
  % the~case~of stochastic PDEs
  % \parencite{Wilson-Renormalization-Group-and-Critical-ETC-Part-I-Pub-1971},
  % \parencite{Kupiainen-Renormalization-Group-and-Stochastic-PDEs-Pub-2016}.
  % Because theory of SsPDEs is very complex, for the~purpose of this talk,
  % we need to simplified a lot and introduce some notation. This notation
  % may not be the most precise, but useful in sketching general problem.

  % We first fix dimension $d$ and denote $d$~dimensional torus by $T^{ d }$.
  % Let $V$ be map transforming space of continuous functions on $T^{ d }$
  % into itself:
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-19}
  %   V: \Ccal( T^{ d } ) \to \Ccal( T^{ d } ).
  % \end{equation}
  % The value of $V$ on function $\varphi \in \Ccal( T^{ d } )$ we will be denoting
  % by $V[ \varphi ]$. The derivative of $k$~order of $V$ at $\varphi$ in the direction
  % of function $\psi$ is defined as
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-20}
  %   D^{ k } V[ \varphi ] \cdot \psi^{ \otimes k } :=
  %   \partial_{ \tau }^{ \, k } \, V[ \varphi + \tau \psi ] |_{ \tau = 0 }.
  % \end{equation}

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Toy example}


  For the~sake of simplicity we will work with an equation without
  time dynamics, which is nonetheless inspired by $\Phi_{ d }^{ \, 4 }$
  theory.
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-21}
    ( 1 - \Delta )^{ \sigma / 2 } \Phi = \eta + \lambda \Phi^{ 3 } - \infty \, \Phi,
  \end{equation}
  where $\Phi \in \Dcal'( \Rbb^{ d } )$. Parameter $\sigma \in ( d / 3, d / 2 ]$ for
  technical reasons. As such $( 1 - \Delta )^{ \sigma / 2 }$ will in general be a well
  defined pseudodifferential operator. The $\eta$ is Gaussian white noise and
  $\infty \, \Phi$ symbolize, that due to presence of $\eta$ we need to ``subtract
  infinity'' from the~ill defined product of distributions $\Phi^{ 3 }$.

  In first step we regularize white noise introducing family of smooth
  functions $\eta_{ \kappa }$, $\kappa \in ( 0, 1 ]$, with property
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-22}
    \lim_{ \kappa \searrow 0 } \eta_{ \kappa } = \eta.
  \end{equation}
  Now $\Phi_{ \kappa }$ is a solution of the equation
  \eqref{eq:Stochastic-quantization-ETC-21} with regularized noise.
  % For the~sake of simplicity we will work with equation without
  % time dynamics, which is nonetheless inspired by $\Phi_{ d }^{ \, 4 }$
  % theory.
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-21}
  %   ( 1 - \Delta )^{ \sigma / 2 } \Phi = \eta + \lambda \Phi^{ 3 } - \infty \Phi,
  % \end{equation}
  % where $\Phi \in \Dcal'( \Rbb^{ d } )$. Parameter $\sigma \in ( d / 3, d / 2 ]$ for
  % technical reasons. As such $( 1 - \Delta )^{ \sigma / 2 }$ will in general well
  % defined pseudodifferential operator. The $\eta$ is Gaussian white noise and
  % $\infty \Phi$ symbolize, that due to presence of $\eta$ we need to ``subtract
  % infinity'' from the~ill defined product of distributions $\Phi^{ 3 }$.

  % In first step we regularize white noise introducing family of smooth
  % functions $\eta_{ \kappa }$, $\kappa \in ( 0, 1 ]$, with property
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-22}
  %   \lim_{ \kappa \searrow 0 } \eta_{ \kappa } = \eta.
  % \end{equation}
  % Now $\Phi_{ \kappa }$ is a solution of the equation
  % \eqref{eq:Niespodziewane-teoretyczne-01} with regularized noise.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Toy example}


  We now need to rewrite our problem as
  \begin{subequations}
    \begin{align}
      \label{eq:Stochastic-quantization-ETC-23-A}
      &( 1 - \Delta )^{ \sigma / 2 } \Phi_{ \kappa } = F_{ \kappa }[ \Phi_{ \kappa } ], \\
      &F_{ \kappa }[ \varphi ] =
        \eta_{ \kappa } + \lambda \varphi_{ \kappa }^{ \, 3 } +
        \sum_{ i = 1 }^{ N( \sigma ) } \lambda^{ i } c_{ \kappa }^{ ( i ) } \varphi,
    \end{align}
  \end{subequations}
  with $N( \sigma ) = \lfloor \sigma / ( 3 \sigma - d ) \rfloor$. We define $F_{ \kappa }$ as
  $F_{ \kappa } : \Ccal( T^{ d } ) \to \Ccal( T^{ d } )$, by imposing boundary
  conditions. The last expression in $F_{ \kappa }$ describe
  standard counter terms that are needed when we take limit $\kappa \searrow 0$.
  Their number grows to infinity as $\sigma \searrow d / 3$.

  Let now $G \in L^{ 1 }( \Rbb^{ d } )$ be fundamental solution of
  $( 1 - \Delta )^{ \sigma / 2 }$:
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-24}
    ( 1 - \Delta )^{ \sigma / 2 } G( x ) = \delta( x ).
  \end{equation}
  Equation \eqref{eq:Stochastic-quantization-ETC-23-A} is now equivalent to
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-25}
    \Phi_{ \kappa } = G * F_{ \kappa }[ \Phi_{ \kappa } ].
  \end{equation}
  % We now need to rewrite our problem as
  % \begin{subequations}
  %   \begin{align}
  %     \label{eq:Stochastic-quantization-ETC-23}
  %     &( 1 - \Delta )^{ \sigma / 2 } \Phi_{ \kappa } = F_{ \kappa }[ \Phi_{ \kappa } ], \\
  %     &F_{ \kappa }[ \varphi ] =
  %       \eta_{ \kappa } + \lambda \varphi_{ \kappa }^{ \, 3 } +
  %       \sum_{ i = 1 }^{ N( \sigma ) } \lambda^{ i } c_{ \kappa }^{ ( i ) } \varphi,
  %   \end{align}
  % \end{subequations}
  % with $N( \sigma ) = \lfloor \sigma / ( 3 \sigma - d ) \rfloor$. We define $F_{ \kappa }$ as
  % $F_{ \kappa } : \Ccal( T^{ d } ) \to \Ccal( T^{ d } )$, by imposing boundary
  % conditions. The last term in $F_{ \kappa }$ of second equation describe
  % standard counter terms that are need when we take limit $\kappa \searrow 0$. As we
  % can see the number of counter terms grow to infinity when $\sigma \searrow d / 3$.
  % We will also interpret

  % Let now $G \in L^{ 1 }( \Rbb^{ d } )$ be fundamental solution of
  % $( 1 - \Delta )^{ \sigma / 2 }$:
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-24}
  %   ( 1 - \Delta )^{ \sigma / 2 } G( x ) = \delta( x ).
  % \end{equation}
  % Equation \eqref{} is now equivalent to
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-25}
  %   \Phi_{ \kappa } = G * F_{ \kappa }[ \Phi_{ \kappa } ].
  % \end{equation}

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Coarse-grained process}


  Next step is to find regularized families of $G_{ \mu }$ and $F_{ \kappa, \, \mu }$,
  such that we have $\mu \in [ 0, 1 ]$, $G_{ \mu } \in L^{ 1 }( \Rbb^{ d } )$,
  $G_{ 0 }$ is equal to fundamental solution of $( 1 - \Delta )^{ \sigma / 2 }$, namely
  $G_{ 0 } = G$, $G_{ 1 } = 0$ and dependents on $\mu$ in sufficient regular
  ways. About $F_{ \kappa, \, \mu }$ we assume that for all $\kappa$ and $\mu$ it is
  polynomial in the fields,
  $F_{ \kappa, \, \mu } : \Ccal( T^{ d } ) \to \Ccal( T^{ d } )$,
  $F_{ \kappa, \, 0 } = F_{ \kappa }$ and depends on both $\kappa$ and $\mu$ in regular way.

  Finding such a family $G_{ \mu }$ is not a problem, the main challenge is to
  find appropriate forms of $F_{ \kappa, \, \mu }$. This unfortunately requires a
  lot of work. In first step we define $\Phi_{ \kappa, \, \mu }$ as
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-26}
    \Phi_{ \kappa, \, \mu } = G_{ \mu } * F_{ \kappa }[ \Phi_{ \kappa } ].
  \end{equation}
  It is basically taking some Wilsonian average of $\Phi_{ \kappa }$, so
  we call it \textbf{coarse-grained process}.
  % Next step is to find regularized families of $G_{ \mu }$ and $F_{ \kappa, \, \mu }$,
  % such that we have $\mu \in [ 0, 1 ]$, $G_{ \mu } \in L^{ 1 }( \Rbb^{ d } )$,
  % $G_{ 0 }$ is equal to fundamental solution of $( 1 - \Delta )^{ \sigma / 2 }$, namely
  % $G_{ 0 } = G$, $G_{ 1 } = 0$ and dependents on $\mu$ in sufficient regular
  % way. About $F_{ \kappa, \, \mu }$ we assume that for all $\kappa$ and $\mu$ it is
  % polynomial in the fields,
  % $F_{ \kappa, \, \mu } : \Ccal( T^{ d } ) \to \Ccal( T^{ d } )$,
  % $F_{ \kappa, \, 0 } = F_{ \kappa }$ and depends on both $\kappa$ and $\mu$ in regular way.

  % Finding such family $G_{ \mu }$ is not a problem, the main challenge is to
  % find appropriate form of $F_{ \kappa, \, \mu }$. This unfortunately requires a lot
  % of work. In first step we define $\Phi_{ \kappa, \, \mu }$ as
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-26}
  %   \Phi_{ \kappa, \, \mu } = G_{ \mu } * F_{ \kappa }[ \Phi_{ \kappa } ].
  % \end{equation}
  % It is basically taking some Wilsonian average of $\Phi_{ \kappa }$, so
  % we call it \textbf{coarse-grained process}.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Effective equations}


  We now define \textbf{remainder} $\omega_{ \kappa, \, \mu }$ by equation
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-27}
    F_{ \kappa }[ \Phi_{ \kappa } ] = F_{ \kappa, \ \mu }[ \Phi_{ \kappa, \, \mu } ] + \omega_{ \kappa, \, \mu }.
  \end{equation}
  As if life wasn't hard enough, we need to define yet another complicated
  function.
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-28}
    H_{ \kappa, \, \mu }[ \varphi ] =
    \partial_{ \mu } F_{ \kappa, \, \mu }[ \varphi ] +
    \text{D} F_{ \kappa, \, \mu }[ \varphi ] \cdot \big( ( \partial_{ \mu } G_{ \mu }) *
    F_{ \kappa, \, \mu }[ \varphi ] ) \big).
  \end{equation}
  We can now write a very important system of \textbf{effective equations}.
  \begin{subequations}
    \begin{align}
      \label{eq:Stochastic-quantization-ETC-29}
      \Phi_{ \kappa, \mu }
      &=
        -\int\limits_{ \mu }^{ 1 } ( \partial_{ \rho } G_{ \rho } ) *
        \big( F_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] + \omega_{ \kappa, \, \rho } \big) \,
        \text{d}\rho, \\
      \omega_{ \kappa, \mu }
      &=
        -\int\limits_{ 0 }^{ \mu } \big( H_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] +
        \text{D} F_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] \cdot
        ( ( \partial_{ \rho } G_{ \rho } ) * \omega_{ \kappa, \rho } ) \big) \, \text{d}\rho.
    \end{align}
  \end{subequations}
  For the details of their derivation you can check lecture notes
  by Paweł Duch ???.
  % We now define \textbf{remainder} $\omega_{ \kappa, \, \mu }$ by equation
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-27}
  %   F_{ \kappa }[ \Phi_{ \kappa } ] = F_{ \kappa, \ \mu }[ \Phi_{ \kappa, \, \mu } ] + \omega_{ \kappa, \, \mu }.
  % \end{equation}
  % As if life wasn't hard enough, we need to define yet another complicated
  % function.
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-28}
  %   H_{ \kappa, \, \mu }[ \varphi ] =
  %   \partial_{ \mu } F_{ \kappa, \, \mu }[ \varphi ] +
  %   \text{D} F_{ \kappa, \, \mu }[ \varphi ] \cdot \big( ( \partial_{ \mu } G_{ \mu }) *
  %   F_{ \kappa, \, \mu }[ \varphi ] ) \big).
  % \end{equation}

  % We can now wrote very important system of \textbf{effective equations}.
  % \begin{subequations}
  %   \begin{align}
  %     \label{eq:Stochastic-quantization-ETC-29}
  %     \Phi_{ \kappa, \mu }
  %     &=
  %       -\int\limits_{ \mu }^{ 1 } ( \partial_{ \rho } G_{ \rho } ) *
  %       \big( F_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] + \omega_{ \kappa, \, \rho } \big) \,
  %                  \text{d}\rho, \\
  %     \omega_{ \kappa, \mu }
  %     &=
  %       -\int\limits_{ 0 }^{ \mu } \big( H_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] +
  %       \text{D} F_{ \kappa, \, \rho }[ \Phi_{ \kappa, \, \rho } ] \cdot
  %       ( ( \partial_{ \rho } G_{ \rho } ) * \omega_{ \kappa, \rho } ) \big) \, \text{d}\rho.
  %   \end{align}
  % \end{subequations}

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{The main idea of Hairer's approach}


  The main idea behind the approach proposed by Martin Hairer in this
  particular context, can be explained as follows. For $\kappa \neq 0$ effective
  equations are equivalent to the equation from which we started, or more
  precisely to
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-30}
    \Phi_{ \kappa, \, \mu } = G_{ \mu } * F_{ \kappa }[ \Phi_{ \kappa } ].
  \end{equation}
  But, this equation breaks down for $\kappa \searrow 0$, while effective equation
  \alert{can} still be meaningful. But, it doesn't came for free
  and we need to find appropriate function $F_{ \kappa, \, \mu }$, obeying condition
  $F_{ \kappa, 0 } = F_{ \kappa }$.

  Paweł Duch proposed to find $F_{ \kappa, \, \mu }$ by deriving flow equations
  for its coefficient and solving them recursively. At is base it is some
  form of well controlled perturbation series, but more close to the spirit
  of Bogoliubov-Epstein-Glasser approach.
  % The main idea behind approach proposed by Martin Hairer in this particular
  % context, can be explained as follow. For $\kappa \neq 0$ effective equations are
  % equivalent to the equation from which we started, or more precisely to
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-30}
  %   \Phi_{ \kappa, \, \mu } = G_{ \mu } * F_{ \kappa }[ \Phi_{ \kappa } ].
  % \end{equation}
  % But, this equation breaks down for $\kappa \searrow 0$, while effective equation
  % \alert{can} still be meaningful. But, it doesn't came for free
  % and we need to find appropriate function $F_{ \kappa, \, \mu }$, obeying condition
  % $F_{ \kappa, 0 } = F_{ \kappa }$.

  % Paweł Duch proposed to find $F_{ \kappa, \, \mu }$ by deriving flow equations
  % for its coefficient and solve if recursively. At is base it is some form
  % of well controlled perturbation series, but more close to the spirit
  % of Bogoliubov-Epstein-Glasser approach.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Flow equation for $F_{ \kappa, \, \mu }$}

  We know that for function $\varphi$, $F_{ \kappa, \, \mu }[ \varphi ]$ is a continuous
  function on $T^{ d }$. But, for technical reasons is better to think about
  it as distribution on the space of Schwartz functions
  $\Scal( \Rbb^{ d } )$. As such we can define $F_{ \kappa, \, \mu }$ by equation
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-31}
    \langle F_{ \kappa, \, \mu }[ \varphi ], \psi \rangle :=
    \sum_{ i = 0 }^{ N } \sum_{ m = 0 }^{ 3i } \lambda^{ i }
    \langle F_{ \kappa, \, \mu }^{ i, \, m }, \psi \otimes \varphi^{ \otimes k } \rangle,
  \end{equation}
  with $F_{ \kappa, \, \mu }^{ i, \, m }
  \in \Scal'\big( ( \Rbb^{ d } )^{ m + 1 } \big)$. Coefficient
  $F_{ \kappa, \, \mu }^{ i, \, m }$, which are tempered distributions, obeys
  flow equations, which unfortunately is extremely complicated, so can only
  show it, without explaining its full meaning. They also have more
  indices that a normal person can handle.
  % We know that for function $\varphi$, $F_{ \kappa, \, \mu }[ \varphi ]$ is a continuous
  % function on $T^{ d }$. But, for technical reasons is better to think about
  % it as distribution on the space of Schwartz functions
  % $\Scal( \Rbb^{ d } )$. As such we can define $F_{ \kappa, \, \mu }$ by equation
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-31}
  %   \langle F_{ \kappa, \, \mu }[ \varphi ], \psi \rangle :=
  %   \sum_{ i = 0 }^{ N } \sum_{ m = 0 }^{ 3i } \lambda^{ i }
  %   \langle F_{ \kappa, \, \mu }^{ i, \, m }, \psi \otimes \varphi^{ \otimes k } \rangle,
  % \end{equation}
  % with $F_{ \kappa, \, \mu }^{ i, \, m }
  % \in \Scal'\big( ( \Rbb^{ d } )^{ m + 1 } \big)$. Coefficient
  % $F_{ \kappa, \, \mu }^{ i, \, m }$, which are tempered distributions, obeys
  % flow equations, which unfortunately is extremely complicated, so can only
  % show it, without explaining its full meaning. They also have more
  % indices that normal person can handle.
  % We know that for function $\varphi$, $F_{ \kappa, \, \mu }[ \varphi ]$ is a continuous
  % function on $T^{ d }$. But, for technical reasons is better to think about
  % it as distribution on the space of Schwartz functions
  % $\Scal( \Rbb^{ d } )$. As such we can define $F_{ \kappa, \, \mu }$ by equation
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-31}
  %   \langle F_{ \kappa, \, \mu }[ \varphi ], \psi \rangle :=
  %   \sum_{ i = 0 }^{ N } \sum_{ m = 0 }^{ 3i } \lambda^{ i }
  %   \langle F_{ \kappa, \, \mu }^{ i, \, m }, \psi \otimes \varphi^{ \otimes k } \rangle,
  % \end{equation}
  % with $F_{ \kappa, \, \mu }^{ i, \, m }
  % \in \Scal'\big( ( \Rbb^{ d } )^{ m + 1 } \big)$. Coefficient
  % $F_{ \kappa, \, \mu }^{ i, \, m }$, which are tempered distributions obeys
  % flow equation, which unfortunately is extremely complicated, so can only
  % show it, without explaining it full meaning.

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Flow equation for $F_{ \kappa, \, \mu }$}


  Flow equation has the form
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-32}
    \partial_{ \mu } F_{ \kappa, \, \mu }^{ i, \, m } =
    -\sum_{ j = 0 }^{ i } \sum_{ k = 0 }^{ m } ( 1 + k )
    B_{ k }( \partial_{ \mu } G_{ \mu }, F_{ \kappa, \mu }^{ j, \, 1 + k },
    F_{ \kappa, \, \mu }^{ i - j, \, m - k } ).
  \end{equation}
  Functions $B_{ k }$ on the right hand side are so complicated and
  hard to explain, that we won't even attempt to do this here. We just
  wrote symbolic expressions for it.
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-33}
    \begin{split}
      & B_{ k }( G, W, U )( x; \text{d}y_{ 1 }, \text{d}y_{ 2 }, \ldots,
      \text{d}y_{ m } ) := \\
      & \hspace{1em} := \frac{ 1 }{ m! } \sum_{ \pi \in \Pcal_{ m } } \;
        \int\limits_{ \Rbb^{ 2 d } } W( x; \text{d}y_{ \pi( 1 ) },
        \text{d}y_{ \pi( 2 ) }, \ldots,  \text{d}y_{ \pi( k ) } ) G( y - z ) \times \\
      & \hspace{8em} \times U( z; \text{d}y_{ \pi( k + 1 ) },
        \text{d}y_{ \pi( k + 2 ) }, \ldots, \text{d}y_{ \pi( m ) } ) \, \text{d}z.
    \end{split}
  \end{equation}
  At this moment you can only trust that this equation has meaning. \\
  It has.
  % Flow equation has the form
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-32}
  %   \partial_{ \mu } F_{ \kappa, \, \mu }^{ i, \, m } =
  %   -\sum_{ j = 0 }^{ i } \sum_{ k = 0 }^{ m } ( 1 + k )
  %   B_{ k }( \partial_{ \mu } G_{ \mu }, F_{ \kappa, \mu }^{ j, \, 1 + k },
  %   F_{ \kappa, \, \mu }^{ i - j, \, m - k } ).
  % \end{equation}
  % Functions $B_{ k }$ on the right hand side are so complicated and
  % hard to explain, that we won't even attempt to do this here. We just
  % wrote symbolic expression for it.
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-33}
  %   \begin{split}
  %     & B_{ k }( G, W, U )( x; \text{d}y_{ 1 }, \text{d}y_{ 2 }, \ldots,
  %     \text{d}y_{ m } ) := \\
  %     & \hspace{1em} := \frac{ 1 }{ m! } \sum_{ \pi \in \Pcal_{ m } } \;
  %       \int\limits_{ \Rbb^{ 2 d } } W( x; \text{d}y_{ \pi( 1 ) },
  %       \text{d}y_{ \pi( 2 ) }, \ldots,  \text{d}y_{ \pi( k ) } ) G( y - z ) \times \\
  %     & \hspace{8em} \times U( z; \text{d}y_{ \pi( k + 1 ) },
  %       \text{d}y_{ \pi( k + 2 ) }, \ldots, \text{d}y_{ \pi( m ) } ) \, \text{d}z.
  %   \end{split}
  % \end{equation}

\end{frame}
% ##################





% ##################
\begin{frame}
  \frametitle{Recursive solution of flow equation}


  Paweł Duch solves this equation by following a recursive procedure
  stated below.

  $0)$ Set $F_{ \kappa, \, \mu }^{ 0, \, 0 } = \eta_{ \kappa }$
  and $F_{ \kappa, \, \mu }^{ i, \, m } = 0$ if $m > 3i$. \\
  $1)$ We assume that $F_{ \kappa, \, \mu }^{ i, \, m }$ were constructed
  for $i < j$ or for $i = j$ and $m > l$, for some $j$ and $l$.
  Then \alert{set} $\partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }$ equal to the
  RHS of flow equation \eqref{eq:Stochastic-quantization-ETC-32}. \\
  $2)$ Define $F_{ \kappa, \, \mu }^{ j, \, l }$ as
  \begin{equation}
    \label{eq:Stochastic-quantization-ETC-34}
    F_{ \kappa, \, \mu }^{ j, \, l } =
    F_{ \kappa }^{ j, \, l } +
    \int\limits_{ 0 }^{ \mu } \partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }.
  \end{equation}
  We must remember that at this moment
  $\partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }$ is only defined by the~RHS of flow
  equation.

  At this moment we want to end our talk, leaving you with the message that
  the theory of SsPDEs is an active field of research that hopefully will
  help us construct more models of QFT at least in $2 + 1$ dimension.
  % Paweł Duch solves this equation by following a recursive procedure
  % stated below.

  % $0)$ Set $F_{ \kappa, \, \mu }^{ 0, \, 0 } = \eta_{ \kappa }$
  % and $F_{ \kappa, \, \mu }^{ i, \, m } = 0$ if $m > 3i$. \\
  % $1)$ We assume that $F_{ \kappa, \, \mu }^{ i, \, m }$ were constructed
  % for $i < j$ or for $i = j$ and $m > l$, for some $j$ and $l$.
  % Then \alert{set} $\partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }$ equal to the
  % RHS of flow equation. \\
  % $2)$ Define $F_{ \kappa, \, \mu }^{ j, \, l }$ as
  % \begin{equation}
  %   \label{eq:Stochastic-quantization-ETC-34}
  %   F_{ \kappa, \, \mu }^{ j, \, l } =
  %   F_{ \kappa }^{ j, \, l } +
  %   \int\limits_{ 0 }^{ \mu } \partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }.
  % \end{equation}
  % We must remember that at this moment
  % $\partial_{ \mu } F_{ \kappa, \, \mu }^{ j, \, l }$ is only defined by RHS of flow equation.

  % At this moment I want to end our talk with the thought, that theory of
  % SsPDEs is active field of research that hopefully help us construct more
  % models of QFT at least in $2 + 1$ dimension.

\end{frame}
% ##################










% ######################################
\appendix
% ######################################





% ######################################
\EndingSlide{Thank you! Questions?}
% ######################################


% % ##################
% \begin{frame}
%   \frametitle{Dlaczego tak jest?}


%   By wyjaśnić przyczyny tego smutnego stanu rzeczy, sięgniemy do przykładu
%   teorii którą nazywamy $\varphi^{ 4 }$. Tutaj będzie potrzebna znajomość teorii
%   dystrybucji Schwartza. Czy mogę założyć jej znajomość u~Państwa?

%   Teoria $\varphi^{ 4 }$ zdefiniowana jest ona przez lagrangian
%   (dla prostoty używamy standardowej w~fizyce teoretycznej konwencji
%   do zapisu stałych fizycznych)

%   \vspace{-1.5em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \begin{split}
%       \Lcal( \varphi )
%       &=
%         \frac{ 1 }{ 2 } \left[ ( \partial_{ t } \varphi( t, \vecx ) )^{ 2 } -
%         ( \partial_{ x } \varphi( t, \vecx ) )^{ 2 } - ( \partial_{ y } \varphi( t, \vecx ) )^{ 2 } -
%         ( \partial_{ z } \varphi( t, \vecx ) )^{ 2 } \right] - \\
%       &\hspace{1em} - \frac{ \lambda }{ 4! } \varphi( t, \vecx )^{ 4 }.
%     \end{split}
%   \end{equation}

%   \vspace{-1.8em}



%   Lagrangian ten prowadzi do równania ruchu
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \begin{split}
%       \partial_{ t }^{ 2 } \varphi( t, \vecx ) - \partial_{ x }^{ 2 } \varphi( t, \vecx ) -
%       \partial_{ y }^{ 2 } \varphi( t, \vecx ) - \partial_{ z }^{ 2 } \varphi( t, \vecx ) +
%       \frac{ \lambda }{ 3! } \varphi( t, \vecx )^{ 3 } = 0.
%     \end{split}
%   \end{equation}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Dlaczego tak jest?}

%   \vspace{-1.5em}


%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \begin{split}
%       \partial_{ t }^{ 2 } \varphi( t, \vecx ) - \partial_{ x }^{ 2 } \varphi( t, \vecx ) -
%       \partial_{ y }^{ 2 } \varphi( t, \vecx ) - \partial_{ z }^{ 2 } \varphi( t, \vecx ) +
%       \frac{ \lambda }{ 3! } \varphi( t, \vecx )^{ 3 } = 0.
%     \end{split}
%   \end{equation}
%   Gdzie jest problem? Większość podręczników do kwantowej teorii pola
%   powie nam, że~pole $\varphi$ jest funkcją o~wartościach operatorowych, czyli
%   $\varphi( t, \vecx )$ dla konkretnego $t$ i~$\vecx$ to operator działający
%   w~pewnej przestrzeni Hilberta. Bardziej dokładna analiza wskazuje,
%   że~takie podejście jest błędne.

%   Pole $\varphi( t, \vecx )$ nie jest funkcją o~wartościach operatorowych,
%   lecz \alert{dystrybucją (temperowaną) w~sensie Schwartza} o~wartościach
%   operatorowych. Z~tego powodu wartość tej dystrybucji w~punkcie
%   $( t, \vecx )$ jest w~ogólności pozbawiona sensu i~notacja
%   $\varphi( t, \vecx )$ jest tylko zbiorem symboli na tablicy, bez głębszej
%   treści. (Trochę przesadzam, ale nie tak bardzo trochę.)

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Czym jest pole kwantowe?}


%   Skoro pole $\varphi$ jest dystrybucją, to jeśli weźmiemy jakąś funkcję
%   klasy Schwartza $f$, to wówczas

%   \vspace{-1.7em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-03}
%     \varphi( f ), \qquad
%     f \in \Scal( \Rbb^{ 3 } ),
%   \end{equation}

%   \vspace{-1.8em}



%   jest operatorem działającym na pewnej przestrzeni Hilberta. Ten fakt
%   jest przyczyną częstego pojawiania~się funkcji klasy Schwartza w~pewnym
%   podręczniku do algebry liniowej, który może mieli Państwo kiedyś w~rękach.

%   Wróćmy do naszego równania ruchu

%   \vspace{-2em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \begin{split}
%       \partial_{ t }^{ 2 } \varphi( t, \vecx ) - \partial_{ x }^{ 2 } \varphi( t, \vecx ) -
%       \partial_{ y }^{ 2 } \varphi( t, \vecx ) - \partial_{ z }^{ 2 } \varphi( t, \vecx ) +
%       \frac{ \lambda }{ 3! } \varphi( t, \vecx )^{ 3 } = 0.
%     \end{split}
%   \end{equation}
%   W~tym równaniu liczymy drugą pochodną dystrybucji, co zawsze ma sens.
%   Potem dodajemy dystrybucje, tutaj też wszystko jest dobrze. Potem
%   podnosimy do \alert{trzeciej potęgi} dystrybucję. Oj, nie jest dobrze.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Mamy duży problem}

%   \vspace{-1.5em}


%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \begin{split}
%       \partial_{ t }^{ 2 } \varphi( t, \vecx ) - \partial_{ x }^{ 2 } \varphi( t, \vecx ) -
%       \partial_{ y }^{ 2 } \varphi( t, \vecx ) - \partial_{ z }^{ 2 } \varphi( t, \vecx ) +
%       \frac{ \lambda }{ 3! } \varphi( t, \vecx )^{ 3 } = 0.
%     \end{split}
%   \end{equation}
%   Samo mnożenie dystrybucji jest w~ogólności niewykonalne, tym bardziej
%   nie można w~ogólności podnieść jej do trzeciej potęgi. Niemniej jeśli
%   kogoś nie interesuje zbytnio matematyczna ścisłość, to może spokojnie
%   rozwijać dalej całą teorię w~oparciu o~to pozbawione matematycznego sensu
%   równanie i~swoją intuicję fizyczną.

%   Ludzie niezadowoleni z~tego stanu rzeczy stworzyli aksjomatyczną kwantową
%   teorię pola i~konstrukcyjną kwantową teorię pola. Aksjomatyczna teoria
%   pola zajmuje~się definiowaniem tego, czym jest pole kwantowe poprzez
%   podanie listy aksjomatów jakie to ma spełnić obiekt, by był polem
%   kwantowym. Jest to ta sama sytuacja, gdy definiujemy grupę poprzez
%   podanie jej własności, jak istnienie elementu $e$, który dla każdego
%   $g \in G$ spełnia warunek $e g = g e = g$.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Mamy kolejny wielki problem}


%   Tak samo jak w~teorii grup, bazując tylko na aksjomatycznej definicji
%   grupy możemy dowodzić pewnych jej własności (np. istnieje tylko jeden
%   element odwrotny), tak samo w~aksjomatycznej kwantowej teorii pola,
%   wychodząc od tych aksjomatów dowodzą własności pól kwantowych.
%   Na obecną chwilę nie ma jednego ogólnie obowiązujący zestaw aksjomatów
%   dla kwantowej teorii pola, z~istniejących warto wymienić
%   \colorhref{https://en.wikipedia.org/wiki/Wightman_axioms}{aksjomaty
%     Wightmana}
%   i~\colorhref{https://ncatlab.org/nlab/show/Osterwalder-Schrader+theorem}{Osterwaldera-Schradera}.

%   Poważna różnica polega na tym, że~mając aksjomaty teorii, grup od razu
%   możemy podać kilka przykładów takich obiektów, podczas gdy podanie
%   konkretnego przykładu pola kwantowego spełniającego zestaw aksjomatów
%   jest niewiarygodnie trudnym zadaniem. Stąd istnieje osobny przedmiot
%   badań, konstrukcyjna kwantowa teoria pola, która zajmuje~się
%   budowanie konkretnych przykładów pól kwantowych spełniających wybrany
%   zestaw aksjomatów.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{I to naprawdę duży problem}


%   Według moje wiedzy, w~roku $2024$ wciąż nie jest znany \alert{żaden}
%   przykład pola kwantowego w~$3 + 1$ wymiarach, które oddziałuje z~pole
%   kwantowym. W~tej liczbie wymiarów znane są przykłady pola kwantowego,
%   które oddziaływuje z~obiektami netwonowskimi, ale nie jesteśmy w~stanie
%   zdefiniować choćby elektrodynamiki kwantowej.

%   Podamy teraz kilka wybranych dat z~historii konstrukcyjnej kwantowej
%   teorii pola.

%   W~latach $1968\text{-}1972$
%   \colorhref{https://en.wikipedia.org/wiki/James\_Glimm}{James Glimm}
%   i~\colorhref{https://en.wikipedia.org/wiki/Arthur\_Jaffe}{Arhtur Jaffe}
%   konstruują teorię $\varphi^{ 4 }$ w~dwóch wymiarach czasoprzestrzennych.

%   $24$ maja $2000$ roku Instytut Matematyki im. Claya ogłasza swoje Problemy
%   Millenijne. Jednym z~nich jest skonstruowanie kwantowej teorii
%   Yanga-Millsa w~$3 + 1$ wymiarach oraz wykazanie, że~posada przerwę masową.
%   Konstrukcja musi spełniać zbiór aksjomatów co najmniej tak
%   silnych jak aksjomaty Wightmana lub Osterwaldera-Schradera.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Najnowsze wyniki}


%   Autorami oficjalnego sformułowania tego Problemu Millenijnego
%   są \colorhref{https://en.wikipedia.org/wiki/Edward\_Witten}{Edward Witten}
%   i~\colorhref{https://en.wikipedia.org/wiki/Arthur\_Jaffe}{Arthur Jaffe}.
%   Jest ono dostępne pod tym
%   \colorhref{https://www.claymath.org/wp-content/uploads/2022/06/yangmills.pdf}{linkiem}.

%   W~$2022$ roku
%   \colorhref{https://sites.google.com/view/ajaychandra/home}{Ajay Chandra},
%   \colorhref{https://ilyachevyrev.wordpress.com/}{Ilya Chevyrev},
%   \colorhref{https://en.wikipedia.org/wiki/Martin_Hairer}{Martin Hairer}
%   i~\colorhref{https://people.math.wisc.edu/~hshen3/}{Hao Shen} publikują
%   na arXivie wysoce niebanalną pracę
%   \colorhref{https://arxiv.org/abs/2201.03487}{\textit{Stochastic
%       quantisation~of Yang-Mills-Higgs in~3D}}
%   \parencite{Chandra-et-al-Stochastic-quantisation-of-Yang-Mills-ETC-Pub-2024},
%   w~której pokazują jak w~pełni ściśle, choć w~dość pokręcony sposób,
%   skonstruować kwantową teorię Yanga-Millsa wraz z~polem Higgsa, w~$2 + 1$
%   wymiarach.

%   Warto dodać, że~Martin Hairer jest laureatem Medalu Fieldsa za rok $2014$
%   i~„Breakthrough Prize in Mathematics” za rok $2021$
%   i~w~\colorhref{https://www.youtube.com/watch?v=4jR8Sg4PYAA}
%   {wywiadzie} dla kanału Tom Rocks Maths z~tego samego roku stwierdził,
%   że~ich metody działają jeśli wymiar przestrzeni jest równy
%   „$3 + 1 - \varepsilon$”, dla $\varepsilon > 0$, zgodnie jednak z~prawem Murphy’ego,
%   załamują~się dokładnie dla $3 + 1$.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Najnowsze wyniki}


%   Były doktorant prof. Herdegena,
%   dr~\colorhref{https://pawelduch.github.io/}{Paweł Duch} jest obecnie
%   członkiem \colorhref{https://www.epfl.ch/labs/propde/members/}{grupy}
%   Martina Hairera na École Polytechnique Fédérale de Lausanne
%   w~Szwajcarii.

%   Poza tym w~konstrukcyjnej kwantowej teorii pola musimy~się
%   zmagać z~takimi przeciwnościami losu jak:
%   \begin{itemize}

%   \item Nieośrodkowe przestrzenie Hilberta. Z~tego powodu wybór przestrzeni
%     Hilberta dyktuje \alert{fizyczne} własności teorii.

%   \item Twierdzenie Haaga o~niemożliwości zbudowania obrazu interakcji
%     (obrazu Dirac’a), na którym opiera~się większość wyliczeń dla Modelu
%     Standardowego. A~przynajmniej~się opierała przez kilka dekad.

%   \item Całki po trajektoriach i~ich nieistnienie w~większości przypadków.

%   \item I~wiele innych.

%   \end{itemize}

% \end{frame}
% % ##################










% % ######################################
% \section{Algebraiczna kwantowa teoria pola}
% % ######################################


% % ##################
% \begin{frame}
%   \frametitle{Czym jest AQFT?}


%   Algebraiczna kwantowa teoria pola jest w~zasadzie jednym z~wariantów
%   aksjomatycznej kwantowej teorii pola. Została ona sformułowana przez
%   Rudolfa Haaga ($1922\text{-}2016$), z~dużym wkładem ~Davida Ruelle’a
%   (ur.~$1935$), w~latach $50$-tych i~$60$-tych XX~wieku. Jej dwie podstawowe
%   idee można ująć w~następujący sposób.
%   \begin{itemize}

%   \item[1)] Zjawiska fizyczne są zlokalizowane w~czasie i~przestrzeni
%     („zasada-bliskiego-działania”).

%   \item[2)] Fundamentalne relacje między kwantowymi obserwablami mają
%     charakter algebraiczny.

%   \end{itemize}

%   Ze względu na drugi punkt, w~\textsc{aqft} pola kwantowe są obiektem
%   drugorzędnym, na pierwszy zaś plan wysuwają~się odpowiednie algebry
%   obserwabli. Jeśli mamy taką algebrę, jesteśmy w~stanie odtworzyć
%   odpowiednie pole kwantowe.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Problemy i~osiągnięcia AQFT}


%   Tak jak wszystkie inne podejścia aksjomatyczne, \textsc{aqft} zmaga~się
%   z~problemem braku modeli konkretnych pól kwantowych. Tym samym nie możemy
%   wyliczyć, powiedzmy, masy protonu jako funkcji kilku mierzalnych
%   parametrów kwarków i~gluonów, w~tym samym sensie, jak nie możemy podać
%   liczby elementów grupy na podstawie jej definicji. To nie jest coś co
%   wynika z~aksjomatów, tylko z~własności konkretnego bytu matematycznego,
%   gdy już określimy go dokładnie (podając jego podstawowe parametry
%   fizyczne).

%   Chromodynamika na sieciach (obliczenia komputerowe) pozwala nam obliczyć
%   masę protonu, ale to~temat na osobne seminarium, prowadzone przez inną
%   osobę.

%   Niemniej, na poziomie wywodzenia z~aksjomatów, \textsc{aqft}~potrafi
%   udowodnić wiele jakościowy rezultatów zgodnych ze światem, który widzimy.
%   Ale brak możliwości obliczenia masy protonu, sprawia, że~nie możemy być
%   z~obecnego stanu rzeczy zadowoleni.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Lokalizacja zjawisk w~czasoprzestrzeni}

%   \vspace{-0.8em}


%   \begin{figure}

%     \centering


%     \begin{tikzpicture}

%       % x axis
%       \draw[axis arrow] (-5,0) -- (5,0);

%       \pic at (5,0) {x mark for horizontal axis 1};


%       % t axis
%       \draw[axis arrow] (0,-2.5) -- (0,4);

%       \pic at (0,4) {t mark for vertical axis 1};



%       % Light cone
%       \fill[color=blue,opacity=0.4] (0,0) -- (3.5,3.5) -- (-3.5,3.5) -- cycle;

%       \fill[color=blue,opacity=0.4] (0,0) -- (2.2,-2.2) -- (-2.2,-2.2) --
%       cycle;

%       \draw[dashed] (2.2,-2.2) -- (-3.5,3.5);

%       \draw[dashed] (-2.2,-2.2) -- (3.5,3.5);



%       % Region number 1
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (1.2,0) (3,-1) (3.5,1.4) (2.5,1.2) };

%       \node[scale=1.3] at (2.3,0.3) {$\Ocal_{ 1 }$};


%       % Region number 2
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (0.8,0) (2.9,-1.5) (4.2,1.8) (1,3) };

%       \node[scale=1.3] at (2.7,1.8) {$\Ocal_{ 2 }$};


%       % Region number 3
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (-1,-0.2) (-2,1.2) (-3,0.3) (-2,-1) };

%       \node[scale=1.3] at (-2,0.5) {$\Ocal_{ 3 }$};


%       % Event reaching form region 3 to region 1
%       \draw[dashed,thick,color=yellowLoc] (-1.3,0) -- (2,3.3);

%       \fill[color=brown] (-1.3,0) circle [radius=0.09];

%       \node[below] at (-1.3,-0.05) {$E$};

%     \end{tikzpicture}

%     \caption{Trzy ograniczone obszary $\Ocal_{ 1 }$, $\Ocal_{ 2 }$
%       i~$\Ocal_{ 3 }$, oraz zjawisko $E$ wysyłające promień światła.}


%   \end{figure}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Lokalizacja zjawisk w~czasoprzestrzeni}


%   Z~punktu widzenia fizyki interpretacja tej zasady jest prosta. Każdy
%   fizyczny pomiar trwa skończony czas i~zajmuje skończony obszar
%   przestrzeni. Jeśli trzeba możemy zmodyfikować ten formalizm, by dopuścić
%   nieskończone obszary, ale to rzadko jest potrzebne.

%   By być dokładnym, z~każdym zjawiskiem fizycznym wiążemy otwarty
%   i~ograniczony (w~sensie $\Rbb^{ 4 }$) podzbiór czasoprzestrzeni
%   Minkowskiego, oznaczamy go przez $\Ocal$, w~którym może on zostać
%   zmierzony. Ponieważ wielkości mierzone są reprezentowane przez pewną
%   algebrę, więc obszarowi temu przypisuje algebrę $\Acal( \Ocal )$.

%   Dobrze, ale na jakim zasadzie działają takie algebry? Standardowo
%   w~mechanice kwantowej stany reprezentują wektory z~przestrzeni
%   Hilberta $\psi \in \Hcal$, zaś obserwable operatory, przykładowo $X = x$ \\
%   i~$P = -i \, \hbar \frac{ d }{ dx }$. Korzystając z~tego, i~nie
%   przejmując~się zbytnio matematyką pokazujemy:

%   \vspace{-2em}



%   \begin{equation}
%     [ X, P ] = XP - PX = i \, \hbar \id.
%   \end{equation}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Algebry $\MathTextFrametitleFGColor{C^{ * }}$}

%   \vspace{-1em}



%   \begin{equation}
%     [ X, P ] = XP - PX = i \, \hbar \id.
%   \end{equation}
%   W~algebraicznej kwantowej teorii pola, jak sama nazwa wskazuje,
%   traktuje takie \alert{algebraiczne} relacje jak te powyżej, jako
%   najbardziej podstawowe własności obserwablami, którymi to obserwablami
%   może być położenie i~pęd elektronu. Przestrzeń Hilberta i~reprezentacja
%   operatorów jako $X = x$ oraz $P = -i \, \hbar \frac{ d }{ dx }$ jest
%   wyprowadzona z~odpowiednich własności algebr.

%   Tutaj potrzebujemy przywołać pojęcie algebry $C^{ * }$. Jej podstawowe
%   cechy to wyabstrahowane własności macierzy kwadratowych $n \times n$
%   o~wyrazach zespolonych. Dokładniej $\Acal$ jest algebrą $C^{ * }$ jeśli:
%   \begin{itemize}

%   \item[1)] $\Acal$ jest przestrzenią wektorową nad $\Cbb$ (dodawanie
%     macierzy i~mnożenie ich przez liczbę).

%   \item[2)] Zdefiniowana jest operacja mnożenia elementów z~$A$ (mnożenie
%     macierzy).

%   \end{itemize}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Algebry $\MathTextFrametitleFGColor{C^{ * }}$}


%   \begin{itemize}

%   \item[2a)] Mnożenie elementów z~$\Acal$ jest łączne.

%   \item[2b)] Mnożenie jest biliniowe
%     \begin{equation}
%       \label{eq:Niespodziewane-teoretyczne-01}
%       A ( \alpha B + \beta C ) = \alpha A B + \beta A C, \quad
%       ( \alpha A + \beta B ) C = \alpha A C + \beta B C.
%     \end{equation}

%     \vspace{-1.5em}



%   \item[3)] Dana jest operacja zwana inwolucją (sprzężenie hermitowskie
%     macierzy).
%     \begin{equation}
%       \label{eq:Niespodziewane-teoretyczne-01}
%       \Acal \ni A \mapsto A^{ * } \in \Acal.
%     \end{equation}

%     \vspace{-1.5em}



%   \item[3a)] Inwolucja posiada następujące własności

%     \vspace{-2em}



%     \begin{subequations}

%       \begin{align}
%         \label{eq:Niespodziewane-teoretyczne-01}
%         ( \alpha A )^{ * } &= \bar{ \alpha } A^{ * }, \\
%         ( A^{ * } )^{ * } &= A, \\
%         ( A + B )^{ * } &= A^{ * } + B^{ * },
%       \end{align}

%     \end{subequations}

%     \vspace{-2em}



%     gdzie $\bar{ \alpha }$ to liczba sprzężona do~$\alpha$.

%   \end{itemize}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Algebry $\MathTextFrametitleFGColor{C^{ * }}$}


%   W~zbiorze macierzy diagonalizowalnych możemy wprowadzić normę wzorem
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \Vert A \Vert = \max\{ \absOne{ \lambda_{ 1 } }, \absOne{ \lambda_{ 2 } }, \ldots,
%     \absOne{ \lambda_{ n } } \},
%   \end{equation}
%   gdzie $\lambda_{ i }$ to jej wartości własne. Jest to norma o~własnościach
%   znanych z~analizy matematycznej, więc zbiór macierze stają~się przestrzeń
%   metryczną. Dla przypadku macierzy niediagonalizowalnej trzeba ten wzór
%   uogólnić, ale nie jest to teraz tak ważne.

%   Wzorując~się na własnościach tej normy, nakładamy na algebry $C^{ * }$
%   następujące warunki.

%   \begin{itemize}

%   \item[4)] $\Acal$ jest przestrzenią unormowaną z~normą $\Vert \cdot \Vert$.

%   \item[4a)] Przy metryce danej przez $\Vert \cdot \Vert$, $\Acal$ jest przestrzenią
%     zupełną.

%   \item[4b)] Norma spełnia dwa dodatkowe warunki.

%     \vspace{-1.7em}



%     \begin{subequations}

%       \begin{align}
%         \label{eq:Niespodziewane-teoretyczne-01}
%         \Vert A B \Vert &\leq \Vert A \Vert \, \Vert B \Vert, \\
%         \Vert A^{ * } A \Vert &= \Vert A \Vert^{ 2 }.
%       \end{align}

%     \end{subequations}


%   \end{itemize}


% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Własności algebr
%     $\MathTextFrametitleFGColor{C^{ * }}$}


%   Bez wnikania w~detale techniczne, każdą algebrę $C^{ * }$ możemy
%   wyposarzyć w~element neutralny mnożenia $\UnitAlg$:
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     A \UnitAlg = \UnitAlg A.
%   \end{equation}
%   Dla elementu algebry $C^{ * }$ możemy zdefiniować jego widmo, obliczać
%   relacje komutacji, przy odpowiednich założeniach zdefiniować rozkład
%   polarny, etc.

%   Teoria ta nie jest prosta dla początkujących, dlatego prof. Patryk Mach
%   kiedyś stwierdził, że~problem z~pewnym podręcznikiem do algebry polega na
%   tym, że~spora część jego materiału to jest teoria algebr $C^{ * }$
%   wyłożona w~specjalny przypadku macierzy.

%   Potrzebować będziemy teraz pojęcia przestrzeni dualnej do przestrzeni
%   wektorowej. Albo jeszcze lepiej dualnej do przestrzeni unormowanej
%   (Banach). Czy mam przypomnieć o~co chodzi?

% \end{frame}
% % ##################






% % ##################
% \begin{frame}
%   \frametitle{Definicja stanów}


%   Niech $\Acal^{ \text{d} }$ będzie przestrzenią dualną do~$\Acal$.
%   Element $\omega \in \Acal^{ \text{d} }$ nazywamy \textbf{stanem}, jeśli

%   \vspace{-2.5em}



%   \begin{subequations}

%     \begin{align}
%       \label{eq:Niespodziewane-teoretyczne-01}
%       \omega( \UnitAlg ) &= 1 \in \Rbb, \\
%       \omega( A^{ * } A ) &\geq 0, \quad
%                             A \in \Acal.
%     \end{align}

%   \end{subequations}

%   \vspace{-2em}



%   W~\textsc{aqft} elementy algebry $\Acal( \Ocal )$ reprezentują wielkości
%   fizyczne mierzalne w~obszarze $\Ocal$, zaś stany reprezentują, co dużo
%   mówić, stany układu fizycznego, którego wielkości mierzymy.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Algebraiczna QFT $\MathTextFrametitleFGColor{\subset}$
%     Lokalna Fizyka Kwantowa}


%   Przykładowo, niech $X \in \Acal( \Ocal )$ będzie obserwablą określającą
%   odpowiadającą położeniu elektronu, zaś $\omega \in \Acal^{ \text{d} }$
%   będzie stanem elektronu, który porusza~się ruchem jednostajnym
%   prostoliniowym. Wówczas
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \langle X \rangle_{ \omega } := \omega( X ),
%   \end{equation}
%   jest wartością oczekiwaną położenia elektronu w~stanie $\omega$, zmierzoną
%   w~obszarze $\Ocal$. W~mechanice kwantowej zapisalibyśmy to jako
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \langle X \rangle_{ \psi } = \langle \psi | X | \psi \rangle = ( \psi, X \psi ).
%   \end{equation}

%   \vspace{-2em}



%   W~tym możemy już w~zasadzie odtworzyć aparat probabilistyczny mechaniki
%   kwantowej.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Konstrukcja GNS}


%   Niezwykle ważny elementem nie tylko teorii algebr $C^{ * }$, i~całej
%   współczesnej matematyki, jest \textbf{konstrukcja \textsc{gns}
%     (Gelfand-Naimark-Segal)}, która mówi,
%   że~jeśli dysponujemy stanem $\omega$ na algebrze $C^{ * }$, to możemy
%   z~niej „wyciągnąć” przestrzeń Hilberta. Nie możemy
%   wchodzić w~to jak dokładnie ona przebiega, powiedzmy pokrótce, że~chodzi
%   o~to, by potraktować element $A, B \in \Acal$ jako wektory przestrzeni
%   Hilberta i~zdefiniować ich iloczyn skalarny wzorem:

%   \vspace{-1.5em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     ( A, B ) := \omega( A^{ * } B ).
%   \end{equation}

%   \vspace{-1.5em}



%   Dla nas ważne jest to, że~dzięki temu, po odpowiednio dużej ilości
%   pracy, możemy odtworzyć standardowy formalizm mechaniki kwantowej.
%   Acz nie jest to takie łatwe jakby się mogło wydawać, tym co nie zgłębili
%   arkanów analizy funkcjonalnej.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Lokalizacja algebr w~czasoprzestrzeni}

%   \vspace{-0.8em}


%   \begin{figure}

%     \centering


%     \begin{tikzpicture}

%       % x axis
%       \draw[axis arrow] (-5,0) -- (5,0);

%       \pic at (5,0) {x mark for horizontal axis 1};


%       % t axis
%       \draw[axis arrow] (0,-2.5) -- (0,4);

%       \pic at (0,4) {t mark for vertical axis 1};



%       % Light cone
%       \fill[color=blue,opacity=0.4] (0,0) -- (3.5,3.5) -- (-3.5,3.5) -- cycle;

%       \fill[color=blue,opacity=0.4] (0,0) -- (2.2,-2.2) -- (-2.2,-2.2) --
%       cycle;

%       \draw[dashed] (2.2,-2.2) -- (-3.5,3.5);

%       \draw[dashed] (-2.2,-2.2) -- (3.5,3.5);



%       % Region number 1
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (1.2,0) (3,-1) (3.5,1.4) (2.5,1.2) };

%       \node[scale=1.3] at (2.5,0.35) {$\Acal( \Ocal_{ 1 } )$};


%       % Region number 2
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (0.8,0) (2.9,-1.5) (4.2,1.8) (1,3) };

%       \node[scale=1.3] at (2.9,1.9) {$\Acal( \Ocal_{ 2 } )$};


%       % Region number 3
%       \draw[dashed] plot[smooth cycle]
%       coordinates { (-1,-0.2) (-2,1.2) (-3,0.3) (-2,-1) };

%       \node[scale=1.3] at (-2.1,0.4) {$\Acal( \Ocal_{ 3 } )$};


%       % Event reaching form region 3 to region 1
%       \draw[dashed,thick,color=yellowLoc] (-1.3,0) -- (2,3.3);

%       \fill[color=brown] (-1.3,0) circle [radius=0.09];

%       \node[below] at (-1.3,-0.05) {$E$};

%     \end{tikzpicture}

%     \caption{Lokalizacja algebr w~czasoprzestrzeni.}


%   \end{figure}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Aksjomaty AQFT}


%   \textbf{A.1. Warunek izotonii.} Ponieważ zbiór $\Ocal_{ 1 }$ zawiera~się
%   $\Ocal_{ 2 }$, więc żądamy by zachodziło
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \Acal( \Ocal_{ 1 } ) \subset \Acal( \Ocal_{ 2 } ).
%   \end{equation}
%   Interpretacja tego jest prosta. Jeśli możemy coś zmierzyć zbiorze
%   $\Ocal_{ 1 }$, to możemy to też zmierzyć w~większym zbiorze $\Ocal_{ 2 }$.

%   \textbf{A.2. Przyczynowość Einsteina.} Zbiory $\Ocal_{ 1 }$ i~$\Ocal_{ 3 }$
%   są tak względem siebie ułożone, że~żaden obiekt podróżujący z~prędkością
%   mniejszą bądź równą $c$, nie może z~jednego dotrzeć do drugiego. Tym
%   samym eksperyment przeprowadzony w~jednym z~nich nie może wpłynąć na
%   eksperyment w~drugim. Przypominając sobie, że~dwie macierze które
%   komutują ze sobą, można jednocześnie zdiagonalizować, żądamy by zachodziło
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     [ A, B ] = 0, \quad
%     A \in \Acal( \Ocal_{ 1 } ), B \in \Acal( \Ocal_{ 3 } ).
%   \end{equation}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Aksjomaty AQFT}


%   \textbf{A.3. Niezmienniczość Poincar\'{e}go.} Niech będzie dany obszar
%   $\Ocal$ i~transformacja Poincar\'{e}go o~nazwie $\rho$, która przekształca
%   go w~obszar $\Ucal$. Żądamy by istniał wówczas izomorfizm $\alpha( \rho )$
%   algebr $C^{ * }$:
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \alpha( \rho ) : \Acal( \Ocal ) \to \Acal( \Ucal ).
%   \end{equation}
%   Izomorfizm $\alpha( \rho )$ musi spełniać pewne dodatkowe warunki, ich postać
%   jest teraz drugorzędna.

  % \textbf{A.4. Dynamika.} Niech $\Ocal \subset \Ucal$ i~niech $\Ocal$
  % zawiera jakiś fragment hiperpłaszczyzny $h$ zdefiniowanej równaniem
  % $t = \const$, taki że
  % \begin{equation}
  %   \label{eq:Niespodziewane-teoretyczne-01}
  %   h \cap \Ocal = h \cap \Ucal.
  % \end{equation}
  % Wówczas żądamy by zachodziło
  % \begin{equation}
  %   \label{eq:Niespodziewane-teoretyczne-01}
  %   \Acal( \Ocal ) = \Acal( \Ucal ).
  % \end{equation}
  % Ten dziwnie wyglądający warunek sprowadza~się do tego, że~jeśli
  % zadamy równaniu falowemu dane początkowe na hiperpłaszczyźnie
  % $t = \const$, to tym samym możemy znaleźć rozwiązanie obowiązujące
  % na całej przestrzeni. W~takim razie musi być możliwe odtworzenie
  % algebry w~całej przestrzeni, jeśli znamy ją na pewnym otwartym otoczeniu
  % $t = \const$.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Aksjomaty AQFT}


  % \textbf{A.3. Niezmienniczość Poincar\'{e}go.} Niech będzie dany obszar
  % $\Ocal$ i~transformacja Poincar\'{e}go o~nazwie $\rho$, która przekształca
  % go w~zbiór $\Ucal$. Żądamy by istniał wówczas izomorfizm $\alpha( \rho )$
  % algebr $C^{ * }$:
  % \begin{equation}
  %   \label{eq:Niespodziewane-teoretyczne-01}
  %   \alpha : \Acal( \Ocal ) \to \Acal( \Ucal ).
  % \end{equation}


%   \textbf{A.4. Dynamika.} Niech $\Ocal \subset \Ucal$ i~niech $\Ocal$
%   zawiera jakiś fragment hiperpłaszczyzny $h$ zdefiniowanej równaniem
%   $t = \const$, taki że

%   \vspace{-1.5em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     h \cap \Ucal \subset \Ocal.
%   \end{equation}

%   \vspace{-2em}



%   Wówczas żądamy by zachodziło

%   \vspace{-1.5em}



%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-01}
%     \Acal( \Ocal ) = \Acal( \Ucal ).
%   \end{equation}

%   \vspace{-1.8em}



%   Ten dziwnie wyglądający warunek sprowadza~się do tego, że~jeśli
%   zadamy równaniu falowemu dane początkowe na hiperpłaszczyźnie
%   $t = \const$, to tym samym możemy znaleźć rozwiązanie obowiązujące
%   na całej przestrzeni. W~takim razie musi być możliwe odtworzenie
%   algebry w~całej przestrzeni, jeśli znamy ją na pewnym otwartym otoczeniu
%   $t = \const$.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Podsumowanie}


%   W~tym momencie podstawowe elementy formalizmu są przedstawione, możemy
%   przystąpić do konkretnych rozważań teoretycznych.

%   Oczywiście, nic nie policzymy w~$3 + 1$ wymiarach, bo żadnego konkretnego
%   modelu nie potrafimy tu zbudować. Pozostaje liczyć na~Martina Hairer
%   i~Paweł Ducha. ;)

%   Jeśli ktoś chce~się czegoś więcej dowiedzieć, to może zapytać prof.
%   Herdegena, albo napisać do mnie pod adres \email. To jest ciekawy temat,
%   o~którym dobrze~się rozmawia.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Koniec}

%   \vspace{7em}


%   \begin{center}

%     \Large

%     Dziękuję bardzo. \\
%     Czy są jakieś pytania?

%   \end{center}

% \end{frame}
% % ##################










% % ######################################
% \appendix
% % ######################################



% % ###################
% \begin{frame}
%   \frametitle{Literatura rozszerzająca}


%   Dobrym wprowadzeniem do zagadnień matematycznej kwantowej teorii
%   pola jest praca Stephen J.~Summersa
%   \colorhref{https://arxiv.org/abs/1203.3991}{\textit{A~Perspective
%       on~Constructive Quantum Field Theory}}, prezentująca historyczny
%   rozwój tej dziedziny
%   \parencite{Summers-Prespective-on-Constructive-ETC-Ver-2016}.

%   Podstawowy wykładem \textsc{aqft} jest książka Rudolpha Haaga
%   \textit{Local Quantum Physics. Fields, Particles, Algebras}
%   \parencite{Haag-Local-Quantum-Physics-Pub-1996}. Obecnie
%   jest ona do ściągnięcia z~tej
%   \colorhref{https://link.springer.com/book/10.1007/978-3-642-61458-3}
%   {strony}. Trzeba zauważyć, że~tekst ten zakłada u~czytelnika dużą wiedzę
%   oraz~umiejętności i~wymaga dogłębnego studiowania.

%   Krótszym, choć wciąż wymagającym wprowadzeniem do tej dziedziny
%   jest artykuł Christophera J.~Fewstera i~Kasi Rejzner
%   \colorhref{https://arxiv.org/abs/1904.04051}{\textit{Algebraic Quantum
%       Field Theory -- an~introduction}}
%   \parencite{Fewster-Rejzner-Algebraic-Quantum-Field-Theory-an-introduction-2019}. Warta uwagi jest również napisana w~formie przeglądu praca
%   Detleva Buchholza i~Klausa Fredenhagena
%   \colorhref{https://arxiv.org/abs/2305.12923}{\textit{{Algebraic quantum
%         field theory: objectives, methods, and results}}}
%   \parencite{Buchholz-Fredenhagen-Algebraic-quantum-field-theory-ETC-2023}.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Literatura rozszerzająca}


%   Wiele można~się też dowiedzieć z~artykułów Rudolfa Haaga dostępnych
%   na serwisie \colorhref{https://arxiv.org/abs/hep-th/0001006}{arXiv}.

%   Standardową pozycją na temat algebr $C^{ * }$ i~ich zastosowania
%   w~fizyce jest książka Ola Brattelego i~Dereka Robinsona
%   \textit{Operator Algebras and~Quantum Statistical Mechanics}
%   \parencite{Bratteli-Robinson-Operator-algebras-ETC-Vol-I-Pub-2002}.
%   Lektura tej książki potrafi być jednak bardzo wymagająca.

%   Warte uwagi jest również dzieło M. Takesakiego
%   \colorhref{https://www.amazon.com/Theory-Operator-Algebras-Non-Commulative-Geometry/dp/354042248X}{\textit{Theory of Operator Algebras}}.

%   Po referencje do innych poruszonych tematów można~się zwrócić
%   pod adres \email.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Konstrukcja teorii swobodnej}


%   Wówczas
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-20}
%     \begin{split}
%       \left\langle F^{ ( 1 ) }, \frac{ 1 }{ 2 } \Delta G^{ ( 1 ) } \right\rangle( \varphi )
%       &=
%         \frac{ 1 }{ 2 }
%         \int d \mathrm{vol}( x ) \, d \mathrm{vol}( y ) \,
%         F^{ ( 1 ) }( \varphi )( x ) \\
%       &\hspace{3em} \times \Delta( x, y ) G^{ ( 1 ) }( \varphi )( y ).
%     \end{split}
%   \end{equation}
%   ma przynajmniej formalny sense. Analogicznie robimy dla wyższych
%   pochodnych.

%   Możemy teraz zdefiniować operację $\star$:
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-21}
%     F \star G =
%     \sum\limits_{ i = 0 }^{ \infty } \frac{ i^{ n } \hbar^{ n } }{ n! }
%     \left\langle F^{ ( n ) }, \left( \tfrac{ 1 }{ 2 } \Delta \right)^{ \otimes n }
%       G^{ ( n ) } \right\rangle.
%     \end{equation}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Konstrukcja teorii swobodnej}

%   Inwolucja.
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-22}
%     F^{ * }( \varphi ) = \overline{ F( \varphi ) }.
%   \end{equation}

%   \textbf{Ważne.}
%   Do końca prezentacji będziemy pracować na poziomie tej algebry.

%   \textbf{Uwaga.}
%   Niemożliwość ograniczania~się do funkcjonałów liniowych wynika
%   z~własności grupy renormalizacji.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Konstrukcja teorii z~oddziaływaniem}


%   Algebra pełnej teorii
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-23}
%     S_{ \mathrm{Full} } = S_{ \mathrm{Free} } + S_{ \mathrm{I} }.
%   \end{equation}
%   Aby otrzymać teorię z~oddziaływaniem potrzebujemy jedynie
%   zmienić iloczyn $\star = \star_{ \mathrm{Free} }$ na
%   $\star_{ \mathrm{I} } = \star_{ \mathrm{Full} }$. Biorąc wzór z teorii
%   rozpraszania, możemy to zrobić za pomocą operatorów M\o llera
%   $R_{ S_{ I } }$:
%   \begin{equation}
%     \label{eq:Niespodziewane-teoretyczne-24}
%     F \star_{ \mathrm{I} } G :=
%     R_{ S_{ \mathrm{I} } }^{ -1 }( R_{ S_{ \mathrm{I} } } F
%     \star R_{ S_{ \mathrm{I} } } G ).
%   \end{equation}
%   Ale aby zdefiniować operatory M\o llera potrzebujemy iloczynu
%   chronologicznego.

%   \textbf{Problem.}
%   Iloczyn chronologiczny wymaga brania iloczynów dystrybucji, co skutkuje
%   pojawieniem się rozbieżności ultrafioletowych.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Rozwinięcie perturbacyjne}

%   \textbf{Zagadnienie renormalizacji.}
%   Czasoprzestrzeń zakrzywiona nie ma określonej przestrzeni pędów,
%   jednak można podać odpowiednią procedurę w przestrzeni położeń.
%   Taką procedurę dla przypadku czasoprzestrzeni Minkowskiego
%   podali Epstain i~Glaser [EG73].

%   Została ona uogólniona na zadane zakrzywione czasoprzestrzenie
%   przez Brunettiego i~Fredenhagena [BF00].

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Rozwinięcie perturbacyjne}


%   Renormalizacja przyczynowa Epstaina-Glasera [EG73].
%   Polega na indukcyjnej konstrukcji iloczynów chronologicznych
%   $\Tcal_{ n }$ przy której nie pojawiają się żadne
%   rozbieżności w~ultrafiolecie. Konkretniej, rządamy by:
%   \begin{itemize}
%     \RaggedRight

%   \item[1.] $\Tcal_{ 0 } = 1$.

%   \item[2.]
%     $\Tcal_{ 1 } = \exp\left( \int d \mathrm{vol}( x ) \,
%       d \mathrm{vol}( y ) \, H( x, y )
%       \frac{ \delta^{ 2 } }{ \delta \varphi( x ) \delta \varphi( y ) } \right)$.

%   \item[3.]
%     $\Tcal_{ n }( F_{ 1 }, \ldots, F_{ n } ) =
%     \Tcal_{ k }( F_{ 1 }, \ldots, F_{ k } )
%     \star \Tcal_{ n - k }( F_{ k + 1 },\ldots, F_{ n } )$ jeżeli funkcjonały
%     $F_{ 1 }, \ldots, F_{ k }$ i~$F_{ k + 1 }, \ldots, F_{ n }$ są
%     „rozdzielone przestrzennie”.

%   \end{itemize}


%   \textbf{Grupa renormalizacji.}
%   Niejednoznaczność powyższej konstrukcji jest scharakteryzowana
%   przez grupę renormalizacji St\"{u}ckelberga-Petermana.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Rozwinięcie perturbacyjne}


%   Formalne rozwiązanie procedury Epstaina-Glasera [FR12]
%   \begin{subequations}
%     \begin{equation}
%       \label{eq:Niespodziewane-teoretyczne-25-A}
%       \Tcal_{ n }( F_{ 1 },\ldots, F_{ n } )( \varphi ) =
%       e^{ \sum_{ i < j } D_{ i, j } } F( \varphi_{ 1 } ) \cdot \ldots
%       \cdot F_{ n }( \varphi_{ n } ) |_{ \varphi_{ 1 } = \ldots = \varphi_{ n } = \varphi }.
%     \end{equation}

%     \vspace{-3em}



%     \begin{equation}
%       \begin{split}
%         D_{ i j }
%         &= i \, \hbar \left\langle \Delta^{ F }, \frac{ \delta^{ 2 } }{ \delta \varphi_{ i } \delta \varphi_{ j } }
%           \right\rangle \\
%         &= i \, \hbar \int d \mathrm{vol}( x ) \, d \mathrm{vol}( y ) \,
%         \Delta^{ F }( x, y ) \frac{ \delta^{ 2 } }{ \delta \varphi_{ i }( x ) \delta \varphi_{ j }( y ) }.
%       \end{split}
%     \end{equation}
%   \end{subequations}

%   Można to oczywiście zapisać za pomocą grafów Feynmana.

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Podsumowanie i~perspektywy}


%   \begin{itemize}
%     \RaggedRight

%   \item Praca na poziomie algebraiczny pozwala ominąć wiele
%     trudności.

%   \item Istnieją prace dotyczące kwasiklasycznej reakcji pola
%     na~czasoprzestrzeń.

%   \item Można w~tym formalizmie opisać klasyczną teorię pola
%     i~wówczas da się otrzymać wyniki o zbieżności badanych
%     szeregów.

%   \item Pełna Renormalizacja Epstaina-Glasera jest dobrze umotywowana
%     fizycznie, lecz w~realnych obliczeniach jest niezwykle skomplikowana.
%     Kluczowe więc dla całego podejścia jest to czy da się uprościć tę
%     część teorii. Najnowsze prace skupiają się nad możliwością użycia
%     kombinacji procedury E-G z~renormalizacją wymiarową, jednak nad
%     zakrzywionych czasoprzestrzeniach wymaga to sformułowania
%     w~reprezentacji położeń. Do tej pory osiągnięto pozytywne efekty
%     w~czasoprzestrzeni Minkowskiego [DFKR13].

%   \end{itemize}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}[standout]


%   { \color{jFrametitleFGColor} Nietypowe problemy mogą wymagać
%     niestandardowych rozwiązań. Czy to konkretne jest właściwe to czas
%     pokaże. }

% \end{frame}
% % ##################
















% % ######################################
% \EndingSlide{Pytania? Dziękuję za uwagę.}
% % ######################################










% % ##################
% \begin{frame}
%   \frametitle{Bibliografia}


%   \begin{itemize}
%     \RaggedRight

%   \item [Fre09] K. Fredenhagen, \textit{The impact of~the~algebraic
%       approach on perturbative quantum field theory}.
%     Wystąpienie na \textit{Algebraic Quantum Field Theory~– the first 50
%       Years}, G\"{o}ttingen 2009.

%   \item [Wal09] R. M. Wald, textit{Axiomatic Quantum Field Theory
%       in~Curved Spacetime}. Wystąpienie na \textit{Algebraic
%       Quantum Field Theory~– the first 50 Years}, G\"{o}ttingen 2009.

%   \item [Haa09] R. Haag, \textit{Local Algebras: A~look back at
%     the~early years and~at~some successes and~missed opportunitie}.
%     Wystąpienie na \textit{Algebraic Quantum Field Theory~– the first 50
%     Years}, G\"{o}ttingen 2009.

%   \item [FR12] K. Fredenhagen, K. Rejzner, \textit{Perturbative
%     algebraic quantum field theory}, arXiv: 1208.1428.

%   \end{itemize}

% \end{frame}
% % ##################





% % ##################
% \begin{frame}
%   \frametitle{Bibliografia}


%   \begin{itemize}
%     \RaggedRight

%   \item [EG73] H. Epstein, V. Glaser, \textit{The role of locality
%     in~perturbation theory}, Ann. Inst. H. Poincar\'{e} A
%     \textbf{19} (1973) 211.

%   \item [BF00] R. Brunetti, K. Fredenhagen, \textit{Microlocal Analysis
%     and~Interacting Quantum Field Theories: Renormalization
%     on~Physical Backgrounds}, Commun.Math.Phys, \textbf{208} (2000)
%     623-661, arXiv: 9903.028.

%   \item [BF09] R. Brunetti, K. Fredenhagen, \textit{Quantum Field
%     Theory on~Curved Backgrounds}, Proceedings of the
%     Kompaktkurs \textit{Quantenfeldtheorie auf gekruemmten Raumzeiten} held
%     at~Universitaet Potsdam, Germany, in 8.-12.10.2007, arXiv:
%     0901.2063.

%   \item [DFKR13] M. D\"{u}etsch, K. Fredenhagen, K. J. Keller,
%     K.~Rejzner, \textit{Dimensional Regularization in Position Space,
%       and~a Forest Formula for Epstein-Glaser Renormalization}, arXiv:
%     1311.5424.

%   \end{itemize}

% \end{frame}
% % ##################










% #####################################################################
% #####################################################################
% Bibliography

\printbibliography





% ############################

% Koniec dokumentu
\end{document}
